---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4433333 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      0.9583333 

--- K = 2 ---
Median Z.ar:        0.1883333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.361667 

--- K = 3 ---
Median Z.ar:        0.09777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.452222 

--- K = 4 ---
Median Z.ar:        0.045 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.505 

--- K = 5 ---
Median Z.ar:        0.04222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.507778 

--- K = 6 ---
Median Z.ar:        0.02777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.9761111 
Score segment:      1.498333 

--- K = 7 ---
Median Z.ar:        0.03333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.7583333 
Score segment:      1.275 

--- K = 8 ---
Median Z.ar:        0.2188889 
Median Beta.ar:     1 
Median Gamma.ar:    0.08 
Score segment:      1.151111 

--- K = 9 ---
Median Z.ar:        0.4 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.05 

## Final Score
Final Score: 11.75944 
', '\n```'))
```
