---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4394444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3811111 
Score segment:      1.118556 

--- K = 2 ---
Median Z.ar:        0.1816667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.584333 

--- K = 3 ---
Median Z.ar:        0.07388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.692111 

--- K = 4 ---
Median Z.ar:        0.05 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.716 

--- K = 5 ---
Median Z.ar:        0.02888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.737111 

--- K = 6 ---
Median Z.ar:        0.02888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.737111 

--- K = 7 ---
Median Z.ar:        0.02833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8144444 
Score segment:      1.552111 

--- K = 8 ---
Median Z.ar:        0.02444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.7394444 
Score segment:      1.481 

--- K = 9 ---
Median Z.ar:        0.04444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3888889 
Score segment:      1.110444 

## Final Score
Final Score: 13.72878 
', '\n```'))
```
