---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 1.25\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.51 
Median Beta.ar:     1 
Median Gamma.ar:    0.38 
Score segment:      1.188 

--- K = 2 ---
Median Z.ar:        0.2327778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.533222 

--- K = 3 ---
Median Z.ar:        0.1077778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.658222 

--- K = 4 ---
Median Z.ar:        0.07611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.689889 

--- K = 5 ---
Median Z.ar:        0.08333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.682667 

--- K = 6 ---
Median Z.ar:        0.03611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.729889 

--- K = 7 ---
Median Z.ar:        0.04277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.8533333 
Score segment:      1.576556 

--- K = 8 ---
Median Z.ar:        0.05888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.5877778 
Score segment:      1.294889 

--- K = 9 ---
Median Z.ar:        0.1066667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3655556 
Score segment:      1.024889 

## Final Score
Final Score: 13.37822 
', '\n```'))
```
