---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7122222 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      1.389667 

--- K = 2 ---
Median Z.ar:        0.5272222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.825222 

--- K = 3 ---
Median Z.ar:        0.4211111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.719111 

--- K = 4 ---
Median Z.ar:        0.3494444 
Median Beta.ar:     1 
Median Gamma.ar:    0.9583333 
Score segment:      1.605778 

--- K = 5 ---
Median Z.ar:        0.3016667 
Median Beta.ar:     1 
Median Gamma.ar:    0.7466667 
Score segment:      1.346333 

--- K = 6 ---
Median Z.ar:        0.2777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6172222 
Score segment:      1.193 

--- K = 7 ---
Median Z.ar:        0.4255556 
Median Beta.ar:     1 
Median Gamma.ar:    0.1644444 
Score segment:      1.027111 

--- K = 8 ---
Median Z.ar:        0.665 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.431 

--- K = 9 ---
Median Z.ar:        0.6761111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.442111 

## Final Score
Final Score: 12.97933 
', '\n```'))
```
