---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 1.25\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.38 
Score segment:      1.061333 

--- K = 2 ---
Median Z.ar:        0.1388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.627111 

--- K = 3 ---
Median Z.ar:        0.07111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.694889 

--- K = 4 ---
Median Z.ar:        0.02666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.739333 

--- K = 5 ---
Median Z.ar:        0.02277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.743222 

--- K = 6 ---
Median Z.ar:        0.01722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.748778 

--- K = 7 ---
Median Z.ar:        0.02833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8066667 
Score segment:      1.544333 

--- K = 8 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    0.675 
Score segment:      1.416 

--- K = 9 ---
Median Z.ar:        0.03888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.1922222 
Score segment:      1.002889 

## Final Score
Final Score: 13.57789 
', '\n```'))
```
