---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4427778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      0.9588889 

--- K = 2 ---
Median Z.ar:        0.1755556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.374444 

--- K = 3 ---
Median Z.ar:        0.08166667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.468333 

--- K = 4 ---
Median Z.ar:        0.035 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.515 

--- K = 5 ---
Median Z.ar:        0.03277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.517222 

--- K = 6 ---
Median Z.ar:        0.02055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.529444 

--- K = 7 ---
Median Z.ar:        0.03833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6255556 
Score segment:      1.137222 

--- K = 8 ---
Median Z.ar:        0.1427778 
Median Beta.ar:     1 
Median Gamma.ar:    0.08833333 
Score segment:      1.218889 

--- K = 9 ---
Median Z.ar:        0.07277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.07666667 
Score segment:      1.300556 

## Final Score
Final Score: 12.02 
', '\n```'))
```
