---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.44 
Median Beta.ar:     1 
Median Gamma.ar:    0.3802778 
Score segment:      1.118278 

--- K = 2 ---
Median Z.ar:        0.2483333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.546333 

--- K = 3 ---
Median Z.ar:        0.07222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.693778 

--- K = 4 ---
Median Z.ar:        0.03277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.733222 

--- K = 5 ---
Median Z.ar:        0.04111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.724889 

--- K = 6 ---
Median Z.ar:        0.02277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.743222 

--- K = 7 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    0.905 
Score segment:      1.646 

--- K = 8 ---
Median Z.ar:        0.03833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6372222 
Score segment:      1.364889 

--- K = 9 ---
Median Z.ar:        0.03277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.2861111 
Score segment:      1.019333 

## Final Score
Final Score: 13.58994 
', '\n```'))
```
