---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8477778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3627778 
Score segment:      1.508556 

--- K = 2 ---
Median Z.ar:        0.775 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      2.073 

--- K = 3 ---
Median Z.ar:        0.6722222 
Median Beta.ar:     1 
Median Gamma.ar:    0.7583333 
Score segment:      1.728556 

--- K = 4 ---
Median Z.ar:        0.6577778 
Median Beta.ar:     1 
Median Gamma.ar:    0.315 
Score segment:      1.270778 

--- K = 5 ---
Median Z.ar:        0.685 
Median Beta.ar:     1 
Median Gamma.ar:    0.03166667 
Score segment:      1.419333 

--- K = 6 ---
Median Z.ar:        0.7133333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.479333 

--- K = 7 ---
Median Z.ar:        0.7905556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.556556 

--- K = 8 ---
Median Z.ar:        0.9155556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.681556 

--- K = 9 ---
Median Z.ar:        0.9533333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.719333 

## Final Score
Final Score: 14.437 
', '\n```'))
```
