---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8138889 
Median Beta.ar:     1 
Median Gamma.ar:    0.1633333 
Score segment:      1.200556 

--- K = 2 ---
Median Z.ar:        0.745 
Median Beta.ar:     1 
Median Gamma.ar:    0.87 
Score segment:      1.265 

--- K = 3 ---
Median Z.ar:        0.6194444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3761111 
Score segment:      0.7933333 

--- K = 4 ---
Median Z.ar:        0.995 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.545 

--- K = 5 ---
Median Z.ar:        0.9944444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.544444 

--- K = 6 ---
Median Z.ar:        0.9938889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.543889 

--- K = 7 ---
Median Z.ar:        0.8238889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.373889 

--- K = 8 ---
Median Z.ar:        0.9933333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.543333 

--- K = 9 ---
Median Z.ar:        0.9933333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.543333 

## Final Score
Final Score: 12.35278 
', '\n```'))
```
