---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 2.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.3783333 
Score segment:      1.187444 

--- K = 2 ---
Median Z.ar:        0.2872222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.585222 

--- K = 3 ---
Median Z.ar:        0.1122222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.653778 

--- K = 4 ---
Median Z.ar:        0.07055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.695444 

--- K = 5 ---
Median Z.ar:        0.04222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.723778 

--- K = 6 ---
Median Z.ar:        0.06388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.9288889 
Score segment:      1.631 

--- K = 7 ---
Median Z.ar:        0.03333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8916667 
Score segment:      1.624333 

--- K = 8 ---
Median Z.ar:        0.06 
Median Beta.ar:     1 
Median Gamma.ar:    0.4511111 
Score segment:      1.157111 

--- K = 9 ---
Median Z.ar:        0.07833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.4011111 
Score segment:      1.088778 

## Final Score
Final Score: 13.34689 
', '\n```'))
```
