---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3872222 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.013889 

--- K = 2 ---
Median Z.ar:        0.2183333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.331667 

--- K = 3 ---
Median Z.ar:        0.05222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.497778 

--- K = 4 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.525 

--- K = 5 ---
Median Z.ar:        0.01333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.536667 

--- K = 6 ---
Median Z.ar:        0.01666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.533333 

--- K = 7 ---
Median Z.ar:        0.01 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.54 

--- K = 8 ---
Median Z.ar:        0.03388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.6244444 
Score segment:      1.140556 

--- K = 9 ---
Median Z.ar:        0.03944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.2694444 
Score segment:      1.141111 

## Final Score
Final Score: 12.26 
', '\n```'))
```
