---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3838889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3788889 
Score segment:      1.060778 

--- K = 2 ---
Median Z.ar:        0.1322222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.633778 

--- K = 3 ---
Median Z.ar:        0.055 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.711 

--- K = 4 ---
Median Z.ar:        0.03166667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.734333 

--- K = 5 ---
Median Z.ar:        0.03222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.733778 

--- K = 6 ---
Median Z.ar:        0.02055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.745444 

--- K = 7 ---
Median Z.ar:        0.01333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.752667 

--- K = 8 ---
Median Z.ar:        0.03944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3394444 
Score segment:      1.066 

--- K = 9 ---
Median Z.ar:        0.02388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.6133333 
Score segment:      1.355444 

## Final Score
Final Score: 13.79322 
', '\n```'))
```
