---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2516667 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.149444 

--- K = 2 ---
Median Z.ar:        0.06555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.484444 

--- K = 3 ---
Median Z.ar:        0.02666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.523333 

--- K = 4 ---
Median Z.ar:        0.01388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.536111 

--- K = 5 ---
Median Z.ar:        0.01388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.536111 

--- K = 6 ---
Median Z.ar:        0.006666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.543333 

--- K = 7 ---
Median Z.ar:        0.007777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.8272222 
Score segment:      1.369444 

--- K = 8 ---
Median Z.ar:        0.01055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.4483333 
Score segment:      0.9911111 

--- K = 9 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.6416667 
Score segment:      1.184444 

## Final Score
Final Score: 12.31778 
', '\n```'))
```
