---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5138889 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.015 

--- K = 2 ---
Median Z.ar:        0.2994444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.250556 

--- K = 3 ---
Median Z.ar:        0.1161111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.433889 

--- K = 4 ---
Median Z.ar:        0.1522222 
Median Beta.ar:     1 
Median Gamma.ar:    0.8911111 
Score segment:      1.288889 

--- K = 5 ---
Median Z.ar:        0.06777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.9688889 
Score segment:      1.451111 

--- K = 6 ---
Median Z.ar:        0.06277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.8205556 
Score segment:      1.307778 

--- K = 7 ---
Median Z.ar:        0.3127778 
Median Beta.ar:     1 
Median Gamma.ar:    0.1177778 
Score segment:      1.019444 

--- K = 8 ---
Median Z.ar:        0.3044444 
Median Beta.ar:     1 
Median Gamma.ar:    0.02333333 
Score segment:      1.122222 

--- K = 9 ---
Median Z.ar:        0.1188889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3327778 
Score segment:      0.9983333 

## Final Score
Final Score: 10.88722 
', '\n```'))
```
