---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5105556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      1.188 

--- K = 2 ---
Median Z.ar:        0.2338889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.532111 

--- K = 3 ---
Median Z.ar:        0.1138889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.652111 

--- K = 4 ---
Median Z.ar:        0.09 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.676 

--- K = 5 ---
Median Z.ar:        0.055 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.711 

--- K = 6 ---
Median Z.ar:        0.02722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.738778 

--- K = 7 ---
Median Z.ar:        0.035 
Median Beta.ar:     1 
Median Gamma.ar:    0.8844444 
Score segment:      1.615444 

--- K = 8 ---
Median Z.ar:        0.1005556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3344444 
Score segment:      0.9998889 

--- K = 9 ---
Median Z.ar:        0.1261111 
Median Beta.ar:     1 
Median Gamma.ar:    0.01222222 
Score segment:      1.095667 

## Final Score
Final Score: 13.209 
', '\n```'))
```
