---
title: "iClusterBayes Summary Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.5\n')
```

# Key Summary Statistics
```{r}
cat(paste0('```\n', '

--- Summary for K = 1 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.4756  0.5022  0.5106  0.5103  0.5183  0.5433 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5800  0.7142  0.6605  0.8028  0.9744 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5633  0.6967  0.6432  0.7817  0.9372 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01333 0.04500 0.07167 0.23781 0.26722 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.02111 0.04556 0.06833 0.20849 0.20597 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01833 0.05278 0.13500 0.33940 0.64000 1.00000 

--- Summary for K = 2 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.2011  0.2267  0.2339  0.2337  0.2411  0.2622 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.3733  0.5606  0.5029  0.6799  0.9450 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.3656  0.5456  0.4855  0.6567  0.8811 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01833 0.44000 0.50420 1.00000 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007778 0.047500 0.331933 0.867778 1.000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.6078  1.0000  0.7684  1.0000  1.0000 

--- Summary for K = 3 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.08667 0.10722 0.11389 0.11446 0.12111 0.14722 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2433  0.4411  0.3999  0.5733  0.9094 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2450  0.4394  0.3915  0.5606  0.8267 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8423  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0005556 0.0100000 0.2863336 0.6888889 1.0000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5361  1.0000  0.7589  1.0000  1.0000 

--- Summary for K = 4 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.05889 0.08056 0.09000 0.09193 0.10222 0.17556 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1006  0.3272  0.3072  0.4733  0.8944 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1033  0.3322  0.3011  0.4678  0.7922 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.6389  0.9322  0.7487  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0000000 0.0005556 0.2911788 0.7334722 1.0000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8727  1.0000  1.0000 

--- Summary for K = 5 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.03000 0.04722 0.05500 0.05704 0.06611 0.13000 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.07833 0.30333 0.28760 0.44986 0.85722 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.08333 0.30944 0.28472 0.44944 0.79500 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.3900  0.6961  0.6303  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.8517  1.0000  1.0000  1.0000  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2636  0.6071  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9500  1.0000  0.8753  1.0000  1.0000 

--- Summary for K = 6 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01111 0.02222 0.02722 0.02860 0.03333 0.11667 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01333 0.23889 0.24079 0.40167 0.83556 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01556 0.24778 0.24003 0.40611 0.72167 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.3889  0.8378  0.6673  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.8578  1.0000  1.0000  1.0000  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2840  0.7331  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9094  1.0000  0.8576  1.0000  1.0000 

--- Summary for K = 7 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01222 0.02889 0.03500 0.03629 0.04167 0.09889 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.004444 0.180833 0.200706 0.345556 0.801667 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.005139 0.190556 0.200348 0.352222 0.715556 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.5289  0.5073  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.2911  1.0000  1.0000  0.9991  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2155  0.3289  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.4161  0.8361  0.6733  1.0000  1.0000 

--- Summary for K = 8 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.06167 0.08889 0.10056 0.10350 0.11500 0.26389 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.006111 0.137778 0.172754 0.293333 0.769444 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.006667 0.138889 0.162609 0.285556 0.652778 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2196  0.4689  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.8717  0.9633  0.9222  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.00000 0.08225 0.00000 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.2689  0.3379  0.6311  1.0000 

--- Summary for K = 9 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.08667 0.11389 0.12611 0.12962 0.14111 0.26222 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.006667 0.078333 0.124902 0.207778 0.719444 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007778 0.087222 0.127678 0.220000 0.557778 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.00000 0.06235 0.00000 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.7567  0.9544  0.8684  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.00000 0.02772 0.00000 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.1976  0.3778  1.0000 
', '\n```'))
```

# Conclusion
and basic statistics for each K (1–9). The `.png` files show Z.ar, beta.ar, 
and gamma.ar distributions.
