---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.51 
Median Beta.ar:     1 
Median Gamma.ar:    0.3783333 
Score segment:      1.186333 

--- K = 2 ---
Median Z.ar:        0.2311111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.534889 

--- K = 3 ---
Median Z.ar:        0.1433333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.622667 

--- K = 4 ---
Median Z.ar:        0.05833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.707667 

--- K = 5 ---
Median Z.ar:        0.05333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.712667 

--- K = 6 ---
Median Z.ar:        0.04666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.9627778 
Score segment:      1.682111 

--- K = 7 ---
Median Z.ar:        0.05333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.7583333 
Score segment:      1.471 

--- K = 8 ---
Median Z.ar:        0.09333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.2983333 
Score segment:      0.971 

--- K = 9 ---
Median Z.ar:        0.3216667 
Median Beta.ar:     1 
Median Gamma.ar:    0.01777778 
Score segment:      1.069889 

## Final Score
Final Score: 12.95822 
', '\n```'))
```
