---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5138889 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.015 

--- K = 2 ---
Median Z.ar:        0.2727778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.277222 

--- K = 3 ---
Median Z.ar:        0.1111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.438889 

--- K = 4 ---
Median Z.ar:        0.08388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.466111 

--- K = 5 ---
Median Z.ar:        0.05111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.498889 

--- K = 6 ---
Median Z.ar:        0.07222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.7494444 
Score segment:      1.227222 

--- K = 7 ---
Median Z.ar:        0.1316667 
Median Beta.ar:     1 
Median Gamma.ar:    0.4683333 
Score segment:      0.8866667 

--- K = 8 ---
Median Z.ar:        0.1116667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3633333 
Score segment:      0.975 

--- K = 9 ---
Median Z.ar:        0.2672222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.182778 

## Final Score
Final Score: 10.96778 
', '\n```'))
```
