---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2527778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.148333 

--- K = 2 ---
Median Z.ar:        0.06055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.489444 

--- K = 3 ---
Median Z.ar:        0.02222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.527778 

--- K = 4 ---
Median Z.ar:        0.01277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.537222 

--- K = 5 ---
Median Z.ar:        0.01222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.537778 

--- K = 6 ---
Median Z.ar:        0.006666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.543333 

--- K = 7 ---
Median Z.ar:        0.005555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.544444 

--- K = 8 ---
Median Z.ar:        0.01277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6133333 
Score segment:      1.150556 

--- K = 9 ---
Median Z.ar:        0.01222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.1611111 
Score segment:      1.276667 

## Final Score
Final Score: 12.75556 
', '\n```'))
```
