---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2494444 
Median Beta.ar:     1 
Median Gamma.ar:    0.38 
Score segment:      0.9274444 

--- K = 2 ---
Median Z.ar:        0.08777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.678222 

--- K = 3 ---
Median Z.ar:        0.02222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.743778 

--- K = 4 ---
Median Z.ar:        0.009444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.756556 

--- K = 5 ---
Median Z.ar:        0.009444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.756556 

--- K = 6 ---
Median Z.ar:        0.008333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.757667 

--- K = 7 ---
Median Z.ar:        0.01111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.805 
Score segment:      1.559889 

--- K = 8 ---
Median Z.ar:        0.008333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8638889 
Score segment:      1.621556 

--- K = 9 ---
Median Z.ar:        0.01 
Median Beta.ar:     1 
Median Gamma.ar:    0.5855556 
Score segment:      1.341556 

## Final Score
Final Score: 14.14322 
', '\n```'))
```
