---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6011111 
Median Beta.ar:     1 
Median Gamma.ar:    0.3775 
Score segment:      1.276611 

--- K = 2 ---
Median Z.ar:        0.325 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.623 

--- K = 3 ---
Median Z.ar:        0.1961111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.569889 

--- K = 4 ---
Median Z.ar:        0.1094444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.656556 

--- K = 5 ---
Median Z.ar:        0.1066667 
Median Beta.ar:     1 
Median Gamma.ar:    0.9894444 
Score segment:      1.648778 

--- K = 6 ---
Median Z.ar:        0.09333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8227778 
Score segment:      1.495444 

--- K = 7 ---
Median Z.ar:        0.1111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.6622222 
Score segment:      1.317111 

--- K = 8 ---
Median Z.ar:        0.7116667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.477667 

--- K = 9 ---
Median Z.ar:        0.1805556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.053444 

## Final Score
Final Score: 13.1185 
', '\n```'))
```
