---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 2.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      1.277444 

--- K = 2 ---
Median Z.ar:        0.3311111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.629111 

--- K = 3 ---
Median Z.ar:        0.2044444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.561556 

--- K = 4 ---
Median Z.ar:        0.1655556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.600444 

--- K = 5 ---
Median Z.ar:        0.1255556 
Median Beta.ar:     1 
Median Gamma.ar:    0.9627778 
Score segment:      1.603222 

--- K = 6 ---
Median Z.ar:        0.1183333 
Median Beta.ar:     1 
Median Gamma.ar:    0.7427778 
Score segment:      1.390444 

--- K = 7 ---
Median Z.ar:        0.26 
Median Beta.ar:     1 
Median Gamma.ar:    0.3355556 
Score segment:      0.8935556 

--- K = 8 ---
Median Z.ar:        0.1488889 
Median Beta.ar:     1 
Median Gamma.ar:    0.5111111 
Score segment:      1.128222 

--- K = 9 ---
Median Z.ar:        0.4655556 
Median Beta.ar:     1 
Median Gamma.ar:    0.001666667 
Score segment:      1.229889 

## Final Score
Final Score: 12.31389 
', '\n```'))
```
