---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7144444 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.216111 

--- K = 2 ---
Median Z.ar:        0.5044444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.154444 

--- K = 3 ---
Median Z.ar:        0.4644444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.114444 

--- K = 4 ---
Median Z.ar:        0.4911111 
Median Beta.ar:     1 
Median Gamma.ar:    0.6566667 
Score segment:      0.7977778 

--- K = 5 ---
Median Z.ar:        0.9877778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.537778 

--- K = 6 ---
Median Z.ar:        0.8216667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.371667 

--- K = 7 ---
Median Z.ar:        0.9855556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.535556 

--- K = 8 ---
Median Z.ar:        0.5972222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.147222 

--- K = 9 ---
Median Z.ar:        0.9288889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.478889 

## Final Score
Final Score: 11.35389 
', '\n```'))
```
