---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7116667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3783333 
Score segment:      1.388 

--- K = 2 ---
Median Z.ar:        0.5211111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.819111 

--- K = 3 ---
Median Z.ar:        0.3988889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.696889 

--- K = 4 ---
Median Z.ar:        0.2988889 
Median Beta.ar:     1 
Median Gamma.ar:    0.9461111 
Score segment:      1.543 

--- K = 5 ---
Median Z.ar:        0.3438889 
Median Beta.ar:     1 
Median Gamma.ar:    0.6161111 
Score segment:      1.258 

--- K = 6 ---
Median Z.ar:        0.5861111 
Median Beta.ar:     1 
Median Gamma.ar:    0.1416667 
Score segment:      1.210444 

--- K = 7 ---
Median Z.ar:        0.49 
Median Beta.ar:     1 
Median Gamma.ar:    0.006666667 
Score segment:      1.249333 

--- K = 8 ---
Median Z.ar:        0.9083333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.674333 

--- K = 9 ---
Median Z.ar:        0.7377778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.503778 

## Final Score
Final Score: 13.34289 
', '\n```'))
```
