---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 2.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4405556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3777778 
Score segment:      1.116333 

--- K = 2 ---
Median Z.ar:        0.1711111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.594889 

--- K = 3 ---
Median Z.ar:        0.05722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.708778 

--- K = 4 ---
Median Z.ar:        0.03 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.736 

--- K = 5 ---
Median Z.ar:        0.01722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.748778 

--- K = 6 ---
Median Z.ar:        0.02888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.737111 

--- K = 7 ---
Median Z.ar:        0.01833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9772222 
Score segment:      1.724889 

--- K = 8 ---
Median Z.ar:        0.02333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.7294444 
Score segment:      1.472111 

--- K = 9 ---
Median Z.ar:        0.035 
Median Beta.ar:     1 
Median Gamma.ar:    0.1705556 
Score segment:      1.028444 

## Final Score
Final Score: 13.86733 
', '\n```'))
```
