---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6044444 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.106111 

--- K = 2 ---
Median Z.ar:        0.3505556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.199444 

--- K = 3 ---
Median Z.ar:        0.1972222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.352778 

--- K = 4 ---
Median Z.ar:        0.1727778 
Median Beta.ar:     1 
Median Gamma.ar:    0.9333333 
Score segment:      1.310556 

--- K = 5 ---
Median Z.ar:        0.1538889 
Median Beta.ar:     1 
Median Gamma.ar:    0.8238889 
Score segment:      1.22 

--- K = 6 ---
Median Z.ar:        0.1466667 
Median Beta.ar:     1 
Median Gamma.ar:    0.6538889 
Score segment:      1.057222 

--- K = 7 ---
Median Z.ar:        0.1655556 
Median Beta.ar:     1 
Median Gamma.ar:    0.2525 
Score segment:      1.031944 

--- K = 8 ---
Median Z.ar:        0.9461111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.496111 

--- K = 9 ---
Median Z.ar:        0.5977778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.147778 

## Final Score
Final Score: 10.92194 
', '\n```'))
```
