---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6 
Median Beta.ar:     1 
Median Gamma.ar:    0.3788889 
Score segment:      1.276889 

--- K = 2 ---
Median Z.ar:        0.3605556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.658556 

--- K = 3 ---
Median Z.ar:        0.1716667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.594333 

--- K = 4 ---
Median Z.ar:        0.1266667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.639333 

--- K = 5 ---
Median Z.ar:        0.1033333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9461111 
Score segment:      1.608778 

--- K = 6 ---
Median Z.ar:        0.2411111 
Median Beta.ar:     1 
Median Gamma.ar:    0.5088889 
Score segment:      1.048 

--- K = 7 ---
Median Z.ar:        0.09166667 
Median Beta.ar:     1 
Median Gamma.ar:    0.7227778 
Score segment:      1.397111 

--- K = 8 ---
Median Z.ar:        0.3072222 
Median Beta.ar:     1 
Median Gamma.ar:    0.1005556 
Score segment:      0.9726667 

--- K = 9 ---
Median Z.ar:        0.2338889 
Median Beta.ar:     1 
Median Gamma.ar:    0.235 
Score segment:      0.7671111 

## Final Score
Final Score: 11.96278 
', '\n```'))
```
