---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 1.25\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7116667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3777778 
Score segment:      1.387444 

--- K = 2 ---
Median Z.ar:        0.5161111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.814111 

--- K = 3 ---
Median Z.ar:        0.3838889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.681889 

--- K = 4 ---
Median Z.ar:        0.355 
Median Beta.ar:     1 
Median Gamma.ar:    0.9544444 
Score segment:      1.607444 

--- K = 5 ---
Median Z.ar:        0.49 
Median Beta.ar:     1 
Median Gamma.ar:    0.4772222 
Score segment:      1.265222 

--- K = 6 ---
Median Z.ar:        0.4066667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3511111 
Score segment:      1.055778 

--- K = 7 ---
Median Z.ar:        0.4066667 
Median Beta.ar:     1 
Median Gamma.ar:    0.2022222 
Score segment:      0.9704444 

--- K = 8 ---
Median Z.ar:        0.4866667 
Median Beta.ar:     1 
Median Gamma.ar:    0.03222222 
Score segment:      1.220444 

--- K = 9 ---
Median Z.ar:        0.835 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.601 

## Final Score
Final Score: 12.60378 
', '\n```'))
```
