---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3883333 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.013333 

--- K = 2 ---
Median Z.ar:        0.1394444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.410556 

--- K = 3 ---
Median Z.ar:        0.045 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.505 

--- K = 4 ---
Median Z.ar:        0.03444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.515556 

--- K = 5 ---
Median Z.ar:        0.03666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.513333 

--- K = 6 ---
Median Z.ar:        0.015 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.535 

--- K = 7 ---
Median Z.ar:        0.02944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.6261111 
Score segment:      1.146667 

--- K = 8 ---
Median Z.ar:        0.02222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.7605556 
Score segment:      1.288333 

--- K = 9 ---
Median Z.ar:        0.095 
Median Beta.ar:     1 
Median Gamma.ar:    0.02777778 
Score segment:      1.327222 

## Final Score
Final Score: 12.255 
', '\n```'))
```
