---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.3777778 
Score segment:      1.059111 

--- K = 2 ---
Median Z.ar:        0.1544444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.611556 

--- K = 3 ---
Median Z.ar:        0.05888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.707111 

--- K = 4 ---
Median Z.ar:        0.02388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.742111 

--- K = 5 ---
Median Z.ar:        0.01388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.752111 

--- K = 6 ---
Median Z.ar:        0.02444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.741556 

--- K = 7 ---
Median Z.ar:        0.01277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.753222 

--- K = 8 ---
Median Z.ar:        0.01777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.7722222 
Score segment:      1.520444 

--- K = 9 ---
Median Z.ar:        0.02111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.5616667 
Score segment:      1.306556 

## Final Score
Final Score: 14.19378 
', '\n```'))
```
