---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.515 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.016667 

--- K = 2 ---
Median Z.ar:        0.2722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.277778 

--- K = 3 ---
Median Z.ar:        0.1227778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.427222 

--- K = 4 ---
Median Z.ar:        0.065 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.485 

--- K = 5 ---
Median Z.ar:        0.03722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.512778 

--- K = 6 ---
Median Z.ar:        0.045 
Median Beta.ar:     1 
Median Gamma.ar:    0.9333333 
Score segment:      1.438333 

--- K = 7 ---
Median Z.ar:        0.04611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.8311111 
Score segment:      1.335 

--- K = 8 ---
Median Z.ar:        0.7061111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.256111 

--- K = 9 ---
Median Z.ar:        0.1116667 
Median Beta.ar:     1 
Median Gamma.ar:    0.08444444 
Score segment:      1.253889 

## Final Score
Final Score: 12.00278 
', '\n```'))
```
