---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5094444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3788889 
Score segment:      1.186333 

--- K = 2 ---
Median Z.ar:        0.2316667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.534333 

--- K = 3 ---
Median Z.ar:        0.1372222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.628778 

--- K = 4 ---
Median Z.ar:        0.05388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.712111 

--- K = 5 ---
Median Z.ar:        0.05111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.714889 

--- K = 6 ---
Median Z.ar:        0.05444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.711556 

--- K = 7 ---
Median Z.ar:        0.08388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.4105556 
Score segment:      1.092667 

--- K = 8 ---
Median Z.ar:        0.04833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6011111 
Score segment:      1.318778 

--- K = 9 ---
Median Z.ar:        0.1361111 
Median Beta.ar:     1 
Median Gamma.ar:    0.2005556 
Score segment:      0.8973333 

## Final Score
Final Score: 12.79678 
', '\n```'))
```
