---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8466667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3638889 
Score segment:      1.508556 

--- K = 2 ---
Median Z.ar:        0.7544444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      2.052444 

--- K = 3 ---
Median Z.ar:        0.6433333 
Median Beta.ar:     1 
Median Gamma.ar:    0.72 
Score segment:      1.661333 

--- K = 4 ---
Median Z.ar:        0.9822222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.748222 

--- K = 5 ---
Median Z.ar:        0.9861111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.752111 

--- K = 6 ---
Median Z.ar:        0.9794444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.745444 

--- K = 7 ---
Median Z.ar:        0.9733333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.739333 

--- K = 8 ---
Median Z.ar:        0.8338889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.599889 

--- K = 9 ---
Median Z.ar:        0.99 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.756 

## Final Score
Final Score: 15.56333 
', '\n```'))
```
