---
title: "iClusterBayes Summary Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 0.2\n')
```

# Key Summary Statistics
```{r}
cat(paste0('```\n', '

--- Summary for K = 1 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.5450  0.8394  0.8467  0.8431  0.8539  0.8756 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5744  0.7156  0.6602  0.8067  0.9811 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5617  0.6989  0.6429  0.7861  0.9544 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01722 0.04556 0.07111 0.23218 0.25556 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.02389 0.04611 0.06889 0.20273 0.20222 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01944 0.05222 0.13111 0.33207 0.61167 1.00000 

--- Summary for K = 2 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.5078  0.7211  0.7544  0.7433  0.7778  0.8111 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2939  0.4844  0.4486  0.6233  0.9578 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2906  0.4747  0.4324  0.6000  0.8678 
  Modality 2 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.009444 0.253333 0.458695 1.000000 1.000000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00500 0.02667 0.29659 0.70681 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.4206  1.0000  0.7326  1.0000  1.0000 

--- Summary for K = 3 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.4911  0.6033  0.6433  0.6389  0.6800  0.7778 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1396  0.3094  0.3078  0.4589  0.9378 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1411  0.3100  0.2988  0.4472  0.8272 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.03722 0.36607 0.92056 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.4628  0.7178  0.7717  0.7891  0.8450  1.0000 
  Modality 4 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.000000 0.001111 0.211558 0.250833 1.000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.7044  1.0000  0.7794  1.0000  1.0000 

--- Summary for K = 4 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.7089  0.9728  0.9822  0.9780  0.9878  0.9983 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.09889 0.25889 0.29688 0.44000 0.92556 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.09167 0.23000 0.23344 0.35500 0.74611 
  Modality 2 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0000000 0.0000000 0.0001952 0.0000000 1.0000000 
  Modality 3 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.000e+00 0.000e+00 0.000e+00 1.765e-05 0.000e+00 1.167e-02 
  Modality 4 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0000000 0.0000000 0.0001049 0.0000000 0.0422222 
  Modality 5 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0000000 0.0000000 0.0001003 0.0000000 0.4950000 

--- Summary for K = 5 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.7250  0.9806  0.9861  0.9833  0.9900  0.9978 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.04944 0.17000 0.21107 0.31389 0.92056 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.05222 0.16778 0.18370 0.28778 0.68444 
  Modality 2 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.00e+00 0.00e+00 0.00e+00 5.47e-05 0.00e+00 1.00e+00 
  Modality 3 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.000e+00 0.000e+00 0.000e+00 2.711e-06 0.000e+00 2.556e-02 
  Modality 4 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.000e+00 0.000e+00 0.000e+00 2.161e-05 0.000e+00 1.667e-02 
  Modality 5 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.000e+00 0.000e+00 0.000e+00 1.097e-05 0.000e+00 9.167e-02 

--- Summary for K = 6 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.7678  0.9717  0.9794  0.9772  0.9850  0.9956 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.02778 0.12222 0.17438 0.25833 0.90444 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0300  0.1222  0.1475  0.2361  0.6272 
  Modality 2 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0000000 0.0000000 0.0001984 0.0000000 1.0000000 
  Modality 3 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0000000 0.0000000 0.0000106 0.0000000 0.2111111 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0       0       0       0       0       0 
  Modality 5 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.000000 0.000000 0.001764 0.000000 1.000000 

--- Summary for K = 7 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.8050  0.9622  0.9733  0.9701  0.9822  0.9956 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01556 0.07611 0.12830 0.18278 0.88778 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01667 0.08000 0.11226 0.17778 0.72056 
  Modality 2 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0000000 0.0000000 0.0002114 0.0000000 1.0000000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0       0       0       0       0       0 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0       0       0       0       0       0 
  Modality 5 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.000000 0.000000 0.002997 0.000000 1.000000 

--- Summary for K = 8 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.6350  0.8044  0.8339  0.8277  0.8561  0.9200 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007778 0.042778 0.082871 0.116667 0.858333 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.008889 0.045556 0.078651 0.122222 0.522222 
  Modality 2 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.000000 0.000000 0.002966 0.000000 1.000000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2113  0.3439  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.00000 0.00085 0.00000 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.00000 0.01893 0.00000 1.00000 

--- Summary for K = 9 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.9111  0.9867  0.9900  0.9889  0.9922  0.9983 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007222 0.032778 0.070198 0.091667 0.882222 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.008333 0.035833 0.065532 0.096667 0.592778 
  Modality 2 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.00e+00 0.00e+00 0.00e+00 3.53e-05 0.00e+00 1.00e+00 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0       0       0       0       0       0 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0       0       0       0       0       0 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0       0       0       0       0       0 
', '\n```'))
```

# Conclusion
and basic statistics for each K (1–9). The `.png` files show Z.ar, beta.ar, 
and gamma.ar distributions.
