---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 1.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.3805556 
Score segment:      1.061889 

--- K = 2 ---
Median Z.ar:        0.1333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.632667 

--- K = 3 ---
Median Z.ar:        0.04333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.722667 

--- K = 4 ---
Median Z.ar:        0.02555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.740444 

--- K = 5 ---
Median Z.ar:        0.02166667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.744333 

--- K = 6 ---
Median Z.ar:        0.01444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.751556 

--- K = 7 ---
Median Z.ar:        0.01 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.756 

--- K = 8 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.7316667 
Score segment:      1.478222 

--- K = 9 ---
Median Z.ar:        0.02111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.4927778 
Score segment:      1.237667 

## Final Score
Final Score: 14.12544 
', '\n```'))
```
