---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5988889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3772222 
Score segment:      1.274111 

--- K = 2 ---
Median Z.ar:        0.3227778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.620778 

--- K = 3 ---
Median Z.ar:        0.1855556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.580444 

--- K = 4 ---
Median Z.ar:        0.1188889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.647111 

--- K = 5 ---
Median Z.ar:        0.1244444 
Median Beta.ar:     1 
Median Gamma.ar:    0.9127778 
Score segment:      1.554333 

--- K = 6 ---
Median Z.ar:        0.1344444 
Median Beta.ar:     1 
Median Gamma.ar:    0.68 
Score segment:      1.311556 

--- K = 7 ---
Median Z.ar:        0.4044444 
Median Beta.ar:     1 
Median Gamma.ar:    0.1775 
Score segment:      0.9929444 

--- K = 8 ---
Median Z.ar:        0.1705556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3933333 
Score segment:      0.9887778 

--- K = 9 ---
Median Z.ar:        0.2405556 
Median Beta.ar:     1 
Median Gamma.ar:    0.1816667 
Score segment:      0.8248889 

## Final Score
Final Score: 11.79494 
', '\n```'))
```
