---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6027778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.103889 

--- K = 2 ---
Median Z.ar:        0.3338889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.216111 

--- K = 3 ---
Median Z.ar:        0.2344444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.315556 

--- K = 4 ---
Median Z.ar:        0.1188889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.431111 

--- K = 5 ---
Median Z.ar:        0.2266667 
Median Beta.ar:     1 
Median Gamma.ar:    0.7016667 
Score segment:      1.025 

--- K = 6 ---
Median Z.ar:        0.11 
Median Beta.ar:     1 
Median Gamma.ar:    0.765 
Score segment:      1.205 

--- K = 7 ---
Median Z.ar:        0.9644444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.514444 

--- K = 8 ---
Median Z.ar:        0.3133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.19 
Score segment:      0.9466667 

--- K = 9 ---
Median Z.ar:        0.8872222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.437222 

## Final Score
Final Score: 11.195 
', '\n```'))
```
