---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7122222 
Median Beta.ar:     1 
Median Gamma.ar:    0.3772222 
Score segment:      1.387444 

--- K = 2 ---
Median Z.ar:        0.5605556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.858556 

--- K = 3 ---
Median Z.ar:        0.4038889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.701889 

--- K = 4 ---
Median Z.ar:        0.3072222 
Median Beta.ar:     1 
Median Gamma.ar:    0.9333333 
Score segment:      1.538556 

--- K = 5 ---
Median Z.ar:        0.3672222 
Median Beta.ar:     1 
Median Gamma.ar:    0.5911111 
Score segment:      1.256333 

--- K = 6 ---
Median Z.ar:        0.4088889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3322222 
Score segment:      1.039111 

--- K = 7 ---
Median Z.ar:        0.4933333 
Median Beta.ar:     1 
Median Gamma.ar:    0.08638889 
Score segment:      1.172944 

--- K = 8 ---
Median Z.ar:        0.6027778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.368778 

--- K = 9 ---
Median Z.ar:        0.8472222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.613222 

## Final Score
Final Score: 12.93683 
', '\n```'))
```
