---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.715 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.216667 

--- K = 2 ---
Median Z.ar:        0.5261111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9283333 
Score segment:      1.104444 

--- K = 3 ---
Median Z.ar:        0.3972222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.152778 

--- K = 4 ---
Median Z.ar:        0.3483333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8494444 
Score segment:      1.051111 

--- K = 5 ---
Median Z.ar:        0.4438889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3788889 
Score segment:      0.6272222 

--- K = 6 ---
Median Z.ar:        0.4111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.23 
Score segment:      0.8088889 

--- K = 7 ---
Median Z.ar:        0.4994444 
Median Beta.ar:     1 
Median Gamma.ar:    0.06222222 
Score segment:      0.9872222 

--- K = 8 ---
Median Z.ar:        0.9605556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.510556 

--- K = 9 ---
Median Z.ar:        0.6894444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.239444 

## Final Score
Final Score: 9.698333 
', '\n```'))
```
