---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8472222 
Median Beta.ar:     1 
Median Gamma.ar:    0.3755556 
Score segment:      1.520778 

--- K = 2 ---
Median Z.ar:        0.7722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      2.070222 

--- K = 3 ---
Median Z.ar:        0.6388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3627778 
Score segment:      1.299667 

--- K = 4 ---
Median Z.ar:        0.6533333 
Median Beta.ar:     1 
Median Gamma.ar:    0.4244444 
Score segment:      1.375778 

--- K = 5 ---
Median Z.ar:        0.6783333 
Median Beta.ar:     1 
Median Gamma.ar:    0.07 
Score segment:      1.374333 

--- K = 6 ---
Median Z.ar:        0.7261111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.492111 

--- K = 7 ---
Median Z.ar:        0.95 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.716 

--- K = 8 ---
Median Z.ar:        0.8938889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.659889 

--- K = 9 ---
Median Z.ar:        0.9027778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.668778 

## Final Score
Final Score: 14.17756 
', '\n```'))
```
