---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8461111 
Median Beta.ar:     1 
Median Gamma.ar:    0.3755556 
Score segment:      1.519667 

--- K = 2 ---
Median Z.ar:        0.7683333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      2.066333 

--- K = 3 ---
Median Z.ar:        0.6772222 
Median Beta.ar:     1 
Median Gamma.ar:    0.7933333 
Score segment:      1.768556 

--- K = 4 ---
Median Z.ar:        0.6577778 
Median Beta.ar:     1 
Median Gamma.ar:    0.2611111 
Score segment:      1.216889 

--- K = 5 ---
Median Z.ar:        0.9822222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.748222 

--- K = 6 ---
Median Z.ar:        0.7111111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.477111 

--- K = 7 ---
Median Z.ar:        0.9833333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.749333 

--- K = 8 ---
Median Z.ar:        0.9216667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.687667 

--- K = 9 ---
Median Z.ar:        0.8783333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.644333 

## Final Score
Final Score: 14.87811 
', '\n```'))
```
