---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8205556 
Median Beta.ar:     1 
Median Gamma.ar:    0.1566667 
Score segment:      1.213889 

--- K = 2 ---
Median Z.ar:        0.7738889 
Median Beta.ar:     1 
Median Gamma.ar:    0.9711111 
Score segment:      1.395 

--- K = 3 ---
Median Z.ar:        0.6627778 
Median Beta.ar:     1 
Median Gamma.ar:    0.2361111 
Score segment:      0.9766667 

--- K = 4 ---
Median Z.ar:        0.9938889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.543889 

--- K = 5 ---
Median Z.ar:        0.9938889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.543889 

--- K = 6 ---
Median Z.ar:        0.9888889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.538889 

--- K = 7 ---
Median Z.ar:        0.8777778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.427778 

--- K = 8 ---
Median Z.ar:        0.9927778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.542778 

--- K = 9 ---
Median Z.ar:        0.9927778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.542778 

## Final Score
Final Score: 12.72556 
', '\n```'))
```
