---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 1.25\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.25 
Median Beta.ar:     1 
Median Gamma.ar:    0.38 
Score segment:      0.928 

--- K = 2 ---
Median Z.ar:        0.05611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.709889 

--- K = 3 ---
Median Z.ar:        0.01555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.750444 

--- K = 4 ---
Median Z.ar:        0.01111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.754889 

--- K = 5 ---
Median Z.ar:        0.01222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.753778 

--- K = 6 ---
Median Z.ar:        0.008333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.757667 

--- K = 7 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.758778 

--- K = 8 ---
Median Z.ar:        0.005 
Median Beta.ar:     1 
Median Gamma.ar:    0.8966667 
Score segment:      1.657667 

--- K = 9 ---
Median Z.ar:        0.008888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.325 
Score segment:      1.082111 

## Final Score
Final Score: 14.15322 
', '\n```'))
```
