---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.25 
Median Beta.ar:     1 
Median Gamma.ar:    0.3772222 
Score segment:      0.9252222 

--- K = 2 ---
Median Z.ar:        0.06111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.704889 

--- K = 3 ---
Median Z.ar:        0.02666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.739333 

--- K = 4 ---
Median Z.ar:        0.01722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.748778 

--- K = 5 ---
Median Z.ar:        0.01 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.756 

--- K = 6 ---
Median Z.ar:        0.004444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.761556 

--- K = 7 ---
Median Z.ar:        0.007777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.758222 

--- K = 8 ---
Median Z.ar:        0.003888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.762111 

--- K = 9 ---
Median Z.ar:        0.006666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.4222222 
Score segment:      1.181556 

## Final Score
Final Score: 14.33767 
', '\n```'))
```
