---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2516667 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.15 

--- K = 2 ---
Median Z.ar:        0.06444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.485556 

--- K = 3 ---
Median Z.ar:        0.03333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.516667 

--- K = 4 ---
Median Z.ar:        0.01444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.535556 

--- K = 5 ---
Median Z.ar:        0.02 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.53 

--- K = 6 ---
Median Z.ar:        0.006666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.543333 

--- K = 7 ---
Median Z.ar:        0.01055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8661111 
Score segment:      1.405556 

--- K = 8 ---
Median Z.ar:        0.01666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.07777778 
Score segment:      1.355556 

--- K = 9 ---
Median Z.ar:        0.03666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.001111111 
Score segment:      1.412222 

## Final Score
Final Score: 12.93444 
', '\n```'))
```
