---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.25 
Median Beta.ar:     1 
Median Gamma.ar:    0.3788889 
Score segment:      0.9268889 

--- K = 2 ---
Median Z.ar:        0.05944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.706556 

--- K = 3 ---
Median Z.ar:        0.02055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.745444 

--- K = 4 ---
Median Z.ar:        0.01555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.750444 

--- K = 5 ---
Median Z.ar:        0.01111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.754889 

--- K = 6 ---
Median Z.ar:        0.006666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.759333 

--- K = 7 ---
Median Z.ar:        0.006111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.759889 

--- K = 8 ---
Median Z.ar:        0.009444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.7438889 
Score segment:      1.500444 

--- K = 9 ---
Median Z.ar:        0.007777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3672222 
Score segment:      1.125444 

## Final Score
Final Score: 14.02933 
', '\n```'))
```
