---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.25 
Median Beta.ar:     1 
Median Gamma.ar:    0.3783333 
Score segment:      0.9263333 

--- K = 2 ---
Median Z.ar:        0.05888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.707111 

--- K = 3 ---
Median Z.ar:        0.02055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.745444 

--- K = 4 ---
Median Z.ar:        0.007777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.758222 

--- K = 5 ---
Median Z.ar:        0.009444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.756556 

--- K = 6 ---
Median Z.ar:        0.006111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.759889 

--- K = 7 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.758778 

--- K = 8 ---
Median Z.ar:        0.007777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.8025 
Score segment:      1.560722 

--- K = 9 ---
Median Z.ar:        0.01111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.2572222 
Score segment:      1.012111 

## Final Score
Final Score: 13.98517 
', '\n```'))
```
