---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2522222 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.148889 

--- K = 2 ---
Median Z.ar:        0.06222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.487778 

--- K = 3 ---
Median Z.ar:        0.02777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.522222 

--- K = 4 ---
Median Z.ar:        0.01166667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.538333 

--- K = 5 ---
Median Z.ar:        0.01 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.54 

--- K = 6 ---
Median Z.ar:        0.006111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.543889 

--- K = 7 ---
Median Z.ar:        0.009444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.540556 

--- K = 8 ---
Median Z.ar:        0.007777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.885 
Score segment:      1.427222 

--- K = 9 ---
Median Z.ar:        0.01055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.2788889 
Score segment:      1.160556 

## Final Score
Final Score: 12.90944 
', '\n```'))
```
