---
title: "iClusterBayes Summary Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.4\n')
```

# Key Summary Statistics
```{r}
cat(paste0('```\n', '

--- Summary for K = 1 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.2167  0.2433  0.2500  0.2501  0.2572  0.2872 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5811  0.7150  0.6614  0.8044  0.9700 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5633  0.6961  0.6430  0.7833  0.9400 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01611 0.04500 0.07167 0.23759 0.26500 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.02000 0.04556 0.06833 0.20802 0.20722 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01500 0.05278 0.13444 0.33904 0.63833 1.00000 

--- Summary for K = 2 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.03833 0.05389 0.05889 0.05855 0.06333 0.07667 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.4144  0.5744  0.5292  0.6861  0.9367 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.4050  0.5589  0.5104  0.6606  0.9089 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01778 0.43611 0.50337 1.00000 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007778 0.047222 0.331605 0.870694 1.000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.6106  1.0000  0.7679  1.0000  1.0000 

--- Summary for K = 3 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.006667 0.017222 0.020556 0.020716 0.023889 0.041667 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2389  0.4350  0.3967  0.5694  0.9233 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2400  0.4322  0.3877  0.5561  0.8522 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9250  1.0000  0.8323  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0005556 0.0105556 0.2915295 0.7436111 1.0000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5811  1.0000  0.7658  1.0000  1.0000 

--- Summary for K = 4 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.001667 0.006111 0.007778 0.007940 0.009444 0.015000 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1806  0.3672  0.3434  0.5050  0.8789 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1856  0.3711  0.3389  0.4989  0.7867 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8371  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.000000 0.003333 0.320229 1.000000 1.000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8946  1.0000  1.0000 

--- Summary for K = 5 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.002222 0.007778 0.009444 0.010802 0.012222 0.055556 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.09514 0.27389 0.27162 0.41611 0.87611 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1000  0.2811  0.2677  0.4133  0.7456 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.4111  1.0000  0.7030  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2889  0.9174  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8867  1.0000  1.0000 

--- Summary for K = 6 ---
Z.ar:
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0005556 0.0044444 0.0061111 0.0064667 0.0077778 0.0405556 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.05611 0.26111 0.25641 0.40500 0.84667 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0600  0.2711  0.2564  0.4100  0.7094 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.4556  0.9961  0.7082  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.3063  0.9397  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8937  1.0000  1.0000 

--- Summary for K = 7 ---
Z.ar:
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0005556 0.0055556 0.0072222 0.0074747 0.0088889 0.0277778 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0400  0.2083  0.2161  0.3406  0.8256 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.04361 0.21889 0.21501 0.34556 0.71722 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.2378  0.4547  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.8956  1.0000  1.0000  1.0000  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2259  0.2757  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.6533  1.0000  0.7690  1.0000  1.0000 

--- Summary for K = 8 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.001111 0.005556 0.007778 0.007925 0.010000 0.020556 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.005556 0.127222 0.160741 0.266667 0.793333 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.006667 0.137778 0.160510 0.276111 0.645000 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.1167  0.4125  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.9971  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.1511  0.0000  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.6900  0.5479  1.0000  1.0000 

--- Summary for K = 9 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.003333 0.008889 0.011111 0.011701 0.013889 0.026111 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007778 0.131667 0.161702 0.266667 0.736111 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.008889 0.144444 0.162192 0.275556 0.629444 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2049  0.3528  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.9948  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.00000 0.07789 0.00000 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.1322  0.3539  0.7506  1.0000 
', '\n```'))
```

# Conclusion
and basic statistics for each K (1–9). The `.png` files show Z.ar, beta.ar, 
and gamma.ar distributions.
