---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 2.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8344444 
Median Beta.ar:     1 
Median Gamma.ar:    0.4794444 
Score segment:      1.611889 

--- K = 2 ---
Median Z.ar:        0.7077778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6955556 
Score segment:      1.701333 

--- K = 3 ---
Median Z.ar:        0.6944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.9594444 
Score segment:      1.951889 

--- K = 4 ---
Median Z.ar:        0.655 
Median Beta.ar:     1 
Median Gamma.ar:    0.385 
Score segment:      1.338 

--- K = 5 ---
Median Z.ar:        0.6855556 
Median Beta.ar:     1 
Median Gamma.ar:    0.003333333 
Score segment:      1.448222 

--- K = 6 ---
Median Z.ar:        0.8283333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.594333 

--- K = 7 ---
Median Z.ar:        0.7816667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.547667 

--- K = 8 ---
Median Z.ar:        0.95 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.716 

--- K = 9 ---
Median Z.ar:        0.9844444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.750444 

## Final Score
Final Score: 14.65978 
', '\n```'))
```
