---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4438889 
Median Beta.ar:     1 
Median Gamma.ar:    0.04944444 
Score segment:      0.9566667 

--- K = 2 ---
Median Z.ar:        0.1744444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.375556 

--- K = 3 ---
Median Z.ar:        0.07888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.471111 

--- K = 4 ---
Median Z.ar:        0.04388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.506111 

--- K = 5 ---
Median Z.ar:        0.03055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.519444 

--- K = 6 ---
Median Z.ar:        0.04 
Median Beta.ar:     1 
Median Gamma.ar:    0.855 
Score segment:      1.365 

--- K = 7 ---
Median Z.ar:        0.02611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9283333 
Score segment:      1.452222 

--- K = 8 ---
Median Z.ar:        0.05055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.6011111 
Score segment:      1.100556 

--- K = 9 ---
Median Z.ar:        0.1633333 
Median Beta.ar:     1 
Median Gamma.ar:    0.08277778 
Score segment:      1.203889 

## Final Score
Final Score: 11.95056 
', '\n```'))
```
