---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.44 
Median Beta.ar:     1 
Median Gamma.ar:    0.3822222 
Score segment:      1.120222 

--- K = 2 ---
Median Z.ar:        0.1855556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.580444 

--- K = 3 ---
Median Z.ar:        0.08111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.684889 

--- K = 4 ---
Median Z.ar:        0.035 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.731 

--- K = 5 ---
Median Z.ar:        0.04333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.722667 

--- K = 6 ---
Median Z.ar:        0.03222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.733778 

--- K = 7 ---
Median Z.ar:        0.04055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.7694444 
Score segment:      1.494889 

--- K = 8 ---
Median Z.ar:        0.02888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.7572222 
Score segment:      1.494333 

--- K = 9 ---
Median Z.ar:        0.03333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.2816667 
Score segment:      1.014333 

## Final Score
Final Score: 13.57656 
', '\n```'))
```
