---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7155556 
Median Beta.ar:     1 
Median Gamma.ar:    0.04722222 
Score segment:      1.218333 

--- K = 2 ---
Median Z.ar:        0.5544444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.204444 

--- K = 3 ---
Median Z.ar:        0.4016667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.148333 

--- K = 4 ---
Median Z.ar:        0.9533333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.503333 

--- K = 5 ---
Median Z.ar:        0.4666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.5105556 
Score segment:      0.6272222 

--- K = 6 ---
Median Z.ar:        0.985 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.535 

--- K = 7 ---
Median Z.ar:        0.6672222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.217222 

--- K = 8 ---
Median Z.ar:        0.9255556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.475556 

--- K = 9 ---
Median Z.ar:        0.9005556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.450556 

## Final Score
Final Score: 11.38 
', '\n```'))
```
