---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7122222 
Median Beta.ar:     1 
Median Gamma.ar:    0.3788889 
Score segment:      1.389111 

--- K = 2 ---
Median Z.ar:        0.51 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.808 

--- K = 3 ---
Median Z.ar:        0.4205556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.718556 

--- K = 4 ---
Median Z.ar:        0.3661111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9316667 
Score segment:      1.595778 

--- K = 5 ---
Median Z.ar:        0.3561111 
Median Beta.ar:     1 
Median Gamma.ar:    0.6272222 
Score segment:      1.281333 

--- K = 6 ---
Median Z.ar:        0.4805556 
Median Beta.ar:     1 
Median Gamma.ar:    0.1866667 
Score segment:      1.059889 

--- K = 7 ---
Median Z.ar:        0.4066667 
Median Beta.ar:     1 
Median Gamma.ar:    0.2083333 
Score segment:      0.9643333 

--- K = 8 ---
Median Z.ar:        0.8977778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.663778 

--- K = 9 ---
Median Z.ar:        0.8605556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.626556 

## Final Score
Final Score: 13.10733 
', '\n```'))
```
