---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3844444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3783333 
Score segment:      1.060778 

--- K = 2 ---
Median Z.ar:        0.1311111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.634889 

--- K = 3 ---
Median Z.ar:        0.04888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.717111 

--- K = 4 ---
Median Z.ar:        0.03111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.734889 

--- K = 5 ---
Median Z.ar:        0.01833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.747667 

--- K = 6 ---
Median Z.ar:        0.01444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.751556 

--- K = 7 ---
Median Z.ar:        0.02888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.7588889 
Score segment:      1.496 

--- K = 8 ---
Median Z.ar:        0.01333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6433333 
Score segment:      1.396 

--- K = 9 ---
Median Z.ar:        0.02055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.5116667 
Score segment:      1.257111 

## Final Score
Final Score: 13.796 
', '\n```'))
```
