---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3855556 
Median Beta.ar:     1 
Median Gamma.ar:    0.04944444 
Score segment:      1.015 

--- K = 2 ---
Median Z.ar:        0.1355556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.414444 

--- K = 3 ---
Median Z.ar:        0.07055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.479444 

--- K = 4 ---
Median Z.ar:        0.02388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.526111 

--- K = 5 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.530556 

--- K = 6 ---
Median Z.ar:        0.01277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.537222 

--- K = 7 ---
Median Z.ar:        0.01611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9466667 
Score segment:      1.480556 

--- K = 8 ---
Median Z.ar:        0.02388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.6816667 
Score segment:      1.207778 

--- K = 9 ---
Median Z.ar:        0.2233333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.226667 

## Final Score
Final Score: 12.41778 
', '\n```'))
```
