---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7127778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3758333 
Score segment:      1.386611 

--- K = 2 ---
Median Z.ar:        0.4938889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.791889 

--- K = 3 ---
Median Z.ar:        0.3833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.681333 

--- K = 4 ---
Median Z.ar:        0.4344444 
Median Beta.ar:     1 
Median Gamma.ar:    0.9161111 
Score segment:      1.648556 

--- K = 5 ---
Median Z.ar:        0.3116667 
Median Beta.ar:     1 
Median Gamma.ar:    0.6833333 
Score segment:      1.293 

--- K = 6 ---
Median Z.ar:        0.8327778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.598778 

--- K = 7 ---
Median Z.ar:        0.3777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3238889 
Score segment:      0.9996667 

--- K = 8 ---
Median Z.ar:        0.7305556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.496556 

--- K = 9 ---
Median Z.ar:        0.9422222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.708222 

## Final Score
Final Score: 13.60461 
', '\n```'))
```
