---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8466667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3833333 
Score segment:      1.528 

--- K = 2 ---
Median Z.ar:        0.7727778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      2.070778 

--- K = 3 ---
Median Z.ar:        0.6666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.6294444 
Score segment:      1.594111 

--- K = 4 ---
Median Z.ar:        0.9827778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.748778 

--- K = 5 ---
Median Z.ar:        0.9838889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.749889 

--- K = 6 ---
Median Z.ar:        0.7361111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.502111 

--- K = 7 ---
Median Z.ar:        0.9866667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.752667 

--- K = 8 ---
Median Z.ar:        0.9866667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.752667 

--- K = 9 ---
Median Z.ar:        0.9888889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.754889 

## Final Score
Final Score: 15.45389 
', '\n```'))
```
