---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 1.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.3772222 
Score segment:      1.388556 

--- K = 2 ---
Median Z.ar:        0.5005556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.798556 

--- K = 3 ---
Median Z.ar:        0.3788889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.676889 

--- K = 4 ---
Median Z.ar:        0.3516667 
Median Beta.ar:     1 
Median Gamma.ar:    0.8866667 
Score segment:      1.536333 

--- K = 5 ---
Median Z.ar:        0.3933333 
Median Beta.ar:     1 
Median Gamma.ar:    0.5711111 
Score segment:      1.262444 

--- K = 6 ---
Median Z.ar:        0.3866667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      1.064111 

--- K = 7 ---
Median Z.ar:        0.465 
Median Beta.ar:     1 
Median Gamma.ar:    0.1094444 
Score segment:      1.121556 

--- K = 8 ---
Median Z.ar:        0.5305556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.296556 

--- K = 9 ---
Median Z.ar:        0.8211111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.587111 

## Final Score
Final Score: 12.73211 
', '\n```'))
```
