---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 2.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2505556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3811111 
Score segment:      0.9296667 

--- K = 2 ---
Median Z.ar:        0.06611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.699889 

--- K = 3 ---
Median Z.ar:        0.02388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.742111 

--- K = 4 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.758778 

--- K = 5 ---
Median Z.ar:        0.01388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.752111 

--- K = 6 ---
Median Z.ar:        0.01222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.753778 

--- K = 7 ---
Median Z.ar:        0.008333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9861111 
Score segment:      1.743778 

--- K = 8 ---
Median Z.ar:        0.007777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.5472222 
Score segment:      1.305444 

--- K = 9 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.7161111 
Score segment:      1.474889 

## Final Score
Final Score: 14.16044 
', '\n```'))
```
