---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6 
Median Beta.ar:     1 
Median Gamma.ar:    0.3772222 
Score segment:      1.275222 

--- K = 2 ---
Median Z.ar:        0.3333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.631333 

--- K = 3 ---
Median Z.ar:        0.155 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.611 

--- K = 4 ---
Median Z.ar:        0.1077778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.658222 

--- K = 5 ---
Median Z.ar:        0.08611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.679889 

--- K = 6 ---
Median Z.ar:        0.05833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9566667 
Score segment:      1.664333 

--- K = 7 ---
Median Z.ar:        0.3183333 
Median Beta.ar:     1 
Median Gamma.ar:    0.2416667 
Score segment:      0.858 

--- K = 8 ---
Median Z.ar:        0.1111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.5516667 
Score segment:      1.206556 

--- K = 9 ---
Median Z.ar:        0.2633333 
Median Beta.ar:     1 
Median Gamma.ar:    0.1327778 
Score segment:      0.8965556 

## Final Score
Final Score: 12.48111 
', '\n```'))
```
