---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.3805556 
Score segment:      1.061889 

--- K = 2 ---
Median Z.ar:        0.135 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.631 

--- K = 3 ---
Median Z.ar:        0.05222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.713778 

--- K = 4 ---
Median Z.ar:        0.05055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.715444 

--- K = 5 ---
Median Z.ar:        0.01555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.750444 

--- K = 6 ---
Median Z.ar:        0.01777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.748222 

--- K = 7 ---
Median Z.ar:        0.01555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.750444 

--- K = 8 ---
Median Z.ar:        0.02055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.6911111 
Score segment:      1.436556 

--- K = 9 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.445 
Score segment:      1.191556 

## Final Score
Final Score: 13.99933 
', '\n```'))
```
