---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3872222 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.013889 

--- K = 2 ---
Median Z.ar:        0.1416667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.408333 

--- K = 3 ---
Median Z.ar:        0.06277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.487222 

--- K = 4 ---
Median Z.ar:        0.02611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.523889 

--- K = 5 ---
Median Z.ar:        0.02222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.527778 

--- K = 6 ---
Median Z.ar:        0.02833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9322222 
Score segment:      1.453889 

--- K = 7 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    0.83 
Score segment:      1.355 

--- K = 8 ---
Median Z.ar:        0.02166667 
Median Beta.ar:     1 
Median Gamma.ar:    0.4166667 
Score segment:      1.011667 

--- K = 9 ---
Median Z.ar:        0.04222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.2394444 
Score segment:      1.168333 

## Final Score
Final Score: 11.95 
', '\n```'))
```
