---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3827778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3805556 
Score segment:      1.061333 

--- K = 2 ---
Median Z.ar:        0.1361111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.629889 

--- K = 3 ---
Median Z.ar:        0.05 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.716 

--- K = 4 ---
Median Z.ar:        0.02944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.736556 

--- K = 5 ---
Median Z.ar:        0.01777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.748222 

--- K = 6 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.746556 

--- K = 7 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.945 
Score segment:      1.691556 

--- K = 8 ---
Median Z.ar:        0.01555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8333333 
Score segment:      1.583778 

--- K = 9 ---
Median Z.ar:        0.03333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.3277778 
Score segment:      1.060444 

## Final Score
Final Score: 13.97433 
', '\n```'))
```
