---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 1.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5088889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      1.186333 

--- K = 2 ---
Median Z.ar:        0.2722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.570222 

--- K = 3 ---
Median Z.ar:        0.1394444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.626556 

--- K = 4 ---
Median Z.ar:        0.07666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.689333 

--- K = 5 ---
Median Z.ar:        0.05333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.712667 

--- K = 6 ---
Median Z.ar:        0.03722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.728778 

--- K = 7 ---
Median Z.ar:        0.04166667 
Median Beta.ar:     1 
Median Gamma.ar:    0.8766667 
Score segment:      1.601 

--- K = 8 ---
Median Z.ar:        0.09888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3633333 
Score segment:      1.030444 

--- K = 9 ---
Median Z.ar:        0.1344444 
Median Beta.ar:     1 
Median Gamma.ar:    0.2522222 
Score segment:      0.8837778 

## Final Score
Final Score: 13.02911 
', '\n```'))
```
