---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8472222 
Median Beta.ar:     1 
Median Gamma.ar:    0.3822222 
Score segment:      1.527444 

--- K = 2 ---
Median Z.ar:        0.7311111 
Median Beta.ar:     1 
Median Gamma.ar:    0.885 
Score segment:      1.914111 

--- K = 3 ---
Median Z.ar:        0.67 
Median Beta.ar:     1 
Median Gamma.ar:    0.7077778 
Score segment:      1.675778 

--- K = 4 ---
Median Z.ar:        0.6377778 
Median Beta.ar:     1 
Median Gamma.ar:    0.2833333 
Score segment:      1.219111 

--- K = 5 ---
Median Z.ar:        0.6872222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.453222 

--- K = 6 ---
Median Z.ar:        0.9672222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.733222 

--- K = 7 ---
Median Z.ar:        0.7927778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.558778 

--- K = 8 ---
Median Z.ar:        0.9877778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.753778 

--- K = 9 ---
Median Z.ar:        0.9827778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.748778 

## Final Score
Final Score: 14.58422 
', '\n```'))
```
