---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5138889 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.015 

--- K = 2 ---
Median Z.ar:        0.2744444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.275556 

--- K = 3 ---
Median Z.ar:        0.115 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.435 

--- K = 4 ---
Median Z.ar:        0.1077778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.442222 

--- K = 5 ---
Median Z.ar:        0.06333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9916667 
Score segment:      1.478333 

--- K = 6 ---
Median Z.ar:        0.07611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.7638889 
Score segment:      1.237778 

--- K = 7 ---
Median Z.ar:        0.285 
Median Beta.ar:     1 
Median Gamma.ar:    0.2505556 
Score segment:      0.9144444 

--- K = 8 ---
Median Z.ar:        0.06166667 
Median Beta.ar:     1 
Median Gamma.ar:    0.5594444 
Score segment:      1.047778 

--- K = 9 ---
Median Z.ar:        0.4405556 
Median Beta.ar:     1 
Median Gamma.ar:    0.08555556 
Score segment:      0.9238889 

## Final Score
Final Score: 10.77 
', '\n```'))
```
