---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5094444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3777778 
Score segment:      1.185222 

--- K = 2 ---
Median Z.ar:        0.2355556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.533556 

--- K = 3 ---
Median Z.ar:        0.08611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.679889 

--- K = 4 ---
Median Z.ar:        0.05722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.708778 

--- K = 5 ---
Median Z.ar:        0.05333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.712667 

--- K = 6 ---
Median Z.ar:        0.05888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.8611111 
Score segment:      1.568222 

--- K = 7 ---
Median Z.ar:        0.05555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.7666667 
Score segment:      1.477111 

--- K = 8 ---
Median Z.ar:        0.055 
Median Beta.ar:     1 
Median Gamma.ar:    0.6416667 
Score segment:      1.352667 

--- K = 9 ---
Median Z.ar:        0.09722222 
Median Beta.ar:     1 
Median Gamma.ar:    0.3716667 
Score segment:      1.040444 

## Final Score
Final Score: 13.25856 
', '\n```'))
```
