---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.3783333 
Score segment:      1.187444 

--- K = 2 ---
Median Z.ar:        0.2755556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.573556 

--- K = 3 ---
Median Z.ar:        0.1172222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.648778 

--- K = 4 ---
Median Z.ar:        0.06833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.697667 

--- K = 5 ---
Median Z.ar:        0.04444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.721556 

--- K = 6 ---
Median Z.ar:        0.05888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.8961111 
Score segment:      1.603222 

--- K = 7 ---
Median Z.ar:        0.03555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.9222222 
Score segment:      1.652667 

--- K = 8 ---
Median Z.ar:        0.04611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.4333333 
Score segment:      1.153222 

--- K = 9 ---
Median Z.ar:        0.07888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3055556 
Score segment:      0.9926667 

## Final Score
Final Score: 13.23078 
', '\n```'))
```
