---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.44 
Median Beta.ar:     1 
Median Gamma.ar:    0.38 
Score segment:      1.118 

--- K = 2 ---
Median Z.ar:        0.1711111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.594889 

--- K = 3 ---
Median Z.ar:        0.06944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.696556 

--- K = 4 ---
Median Z.ar:        0.03 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.736 

--- K = 5 ---
Median Z.ar:        0.04 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.726 

--- K = 6 ---
Median Z.ar:        0.04055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8605556 
Score segment:      1.586 

--- K = 7 ---
Median Z.ar:        0.02666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.9138889 
Score segment:      1.653222 

--- K = 8 ---
Median Z.ar:        0.03444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.4277778 
Score segment:      1.159333 

--- K = 9 ---
Median Z.ar:        0.04166667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3216667 
Score segment:      1.046 

## Final Score
Final Score: 13.316 
', '\n```'))
```
