---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.44 
Median Beta.ar:     1 
Median Gamma.ar:    0.3805556 
Score segment:      1.118556 

--- K = 2 ---
Median Z.ar:        0.1733333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.592667 

--- K = 3 ---
Median Z.ar:        0.06222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.703778 

--- K = 4 ---
Median Z.ar:        0.04722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.718778 

--- K = 5 ---
Median Z.ar:        0.03111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.734889 

--- K = 6 ---
Median Z.ar:        0.02277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.743222 

--- K = 7 ---
Median Z.ar:        0.02222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.94 
Score segment:      1.683778 

--- K = 8 ---
Median Z.ar:        0.02444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.6716667 
Score segment:      1.413222 

--- K = 9 ---
Median Z.ar:        0.03277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3105556 
Score segment:      1.043778 

## Final Score
Final Score: 13.75267 
', '\n```'))
```
