---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4427778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      0.9583333 

--- K = 2 ---
Median Z.ar:        0.1911111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.358889 

--- K = 3 ---
Median Z.ar:        0.07722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.472778 

--- K = 4 ---
Median Z.ar:        0.03444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.515556 

--- K = 5 ---
Median Z.ar:        0.03 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.52 

--- K = 6 ---
Median Z.ar:        0.02 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.53 

--- K = 7 ---
Median Z.ar:        0.02944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.8305556 
Score segment:      1.351111 

--- K = 8 ---
Median Z.ar:        0.04055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.4155556 
Score segment:      0.9938889 

--- K = 9 ---
Median Z.ar:        0.4016667 
Median Beta.ar:     1 
Median Gamma.ar:    0.04222222 
Score segment:      1.006111 

## Final Score
Final Score: 11.70667 
', '\n```'))
```
