---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4394444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3811111 
Score segment:      1.118556 

--- K = 2 ---
Median Z.ar:        0.2577778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.555778 

--- K = 3 ---
Median Z.ar:        0.1066667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.659333 

--- K = 4 ---
Median Z.ar:        0.05055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.715444 

--- K = 5 ---
Median Z.ar:        0.02944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.736556 

--- K = 6 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.741 

--- K = 7 ---
Median Z.ar:        0.02222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.9866667 
Score segment:      1.730444 

--- K = 8 ---
Median Z.ar:        0.01722222 
Median Beta.ar:     1 
Median Gamma.ar:    0.8916667 
Score segment:      1.640444 

--- K = 9 ---
Median Z.ar:        0.02833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6488889 
Score segment:      1.386556 

## Final Score
Final Score: 14.28411 
', '\n```'))
```
