---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4427778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      0.9583333 

--- K = 2 ---
Median Z.ar:        0.2677778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.282222 

--- K = 3 ---
Median Z.ar:        0.08944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.460556 

--- K = 4 ---
Median Z.ar:        0.03555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.514444 

--- K = 5 ---
Median Z.ar:        0.04111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.508889 

--- K = 6 ---
Median Z.ar:        0.03111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9727778 
Score segment:      1.491667 

--- K = 7 ---
Median Z.ar:        0.03888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.76 
Score segment:      1.271111 

--- K = 8 ---
Median Z.ar:        0.03388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.7172222 
Score segment:      1.233333 

--- K = 9 ---
Median Z.ar:        0.1338889 
Median Beta.ar:     1 
Median Gamma.ar:    0.2077778 
Score segment:      1.108333 

## Final Score
Final Score: 11.82889 
', '\n```'))
```
