---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5994444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3805556 
Score segment:      1.278 

--- K = 2 ---
Median Z.ar:        0.3983333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.696333 

--- K = 3 ---
Median Z.ar:        0.1933333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.572667 

--- K = 4 ---
Median Z.ar:        0.1377778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.628222 

--- K = 5 ---
Median Z.ar:        0.08222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.683778 

--- K = 6 ---
Median Z.ar:        0.2566667 
Median Beta.ar:     1 
Median Gamma.ar:    0.4488889 
Score segment:      1.003556 

--- K = 7 ---
Median Z.ar:        0.1133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6816667 
Score segment:      1.334333 

--- K = 8 ---
Median Z.ar:        0.1677778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3916667 
Score segment:      0.9898889 

--- K = 9 ---
Median Z.ar:        0.2877778 
Median Beta.ar:     1 
Median Gamma.ar:    0.1088889 
Score segment:      0.9448889 

## Final Score
Final Score: 12.13167 
', '\n```'))
```
