---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6033333 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.105 

--- K = 2 ---
Median Z.ar:        0.4422222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.107778 

--- K = 3 ---
Median Z.ar:        0.2355556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.314444 

--- K = 4 ---
Median Z.ar:        0.1322222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.417778 

--- K = 5 ---
Median Z.ar:        0.1533333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8066667 
Score segment:      1.203333 

--- K = 6 ---
Median Z.ar:        0.2805556 
Median Beta.ar:     1 
Median Gamma.ar:    0.4347222 
Score segment:      0.7347222 

--- K = 7 ---
Median Z.ar:        0.1777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3083333 
Score segment:      0.9638889 

--- K = 8 ---
Median Z.ar:        0.4472222 
Median Beta.ar:     1 
Median Gamma.ar:    0.06111111 
Score segment:      0.9416667 

--- K = 9 ---
Median Z.ar:        0.5738889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.123889 

## Final Score
Final Score: 9.9125 
', '\n```'))
```
