---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5994444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3822222 
Score segment:      1.279667 

--- K = 2 ---
Median Z.ar:        0.3938889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.691889 

--- K = 3 ---
Median Z.ar:        0.1994444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.566556 

--- K = 4 ---
Median Z.ar:        0.135 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.631 

--- K = 5 ---
Median Z.ar:        0.1133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9561111 
Score segment:      1.608778 

--- K = 6 ---
Median Z.ar:        0.08166667 
Median Beta.ar:     1 
Median Gamma.ar:    0.8738889 
Score segment:      1.558222 

--- K = 7 ---
Median Z.ar:        0.1461111 
Median Beta.ar:     1 
Median Gamma.ar:    0.59 
Score segment:      1.209889 

--- K = 8 ---
Median Z.ar:        0.1961111 
Median Beta.ar:     1 
Median Gamma.ar:    0.2927778 
Score segment:      0.8626667 

--- K = 9 ---
Median Z.ar:        0.35 
Median Beta.ar:     1 
Median Gamma.ar:    0.1477778 
Score segment:      0.9682222 

## Final Score
Final Score: 12.37689 
', '\n```'))
```
