---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6044444 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.106111 

--- K = 2 ---
Median Z.ar:        0.415 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.135 

--- K = 3 ---
Median Z.ar:        0.2538889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.296111 

--- K = 4 ---
Median Z.ar:        0.115 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.435 

--- K = 5 ---
Median Z.ar:        0.3455556 
Median Beta.ar:     1 
Median Gamma.ar:    0.435 
Score segment:      0.6694444 

--- K = 6 ---
Median Z.ar:        0.5666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.04111111 
Score segment:      1.075556 

--- K = 7 ---
Median Z.ar:        0.1583333 
Median Beta.ar:     1 
Median Gamma.ar:    0.3683333 
Score segment:      0.9233333 

--- K = 8 ---
Median Z.ar:        0.3227778 
Median Beta.ar:     1 
Median Gamma.ar:    0.1055556 
Score segment:      1.021667 

--- K = 9 ---
Median Z.ar:        0.9727778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.522778 

## Final Score
Final Score: 10.185 
', '\n```'))
```
