---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7122222 
Median Beta.ar:     1 
Median Gamma.ar:    0.375 
Score segment:      1.385222 

--- K = 2 ---
Median Z.ar:        0.5488889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.846889 

--- K = 3 ---
Median Z.ar:        0.405 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.703 

--- K = 4 ---
Median Z.ar:        0.32 
Median Beta.ar:     1 
Median Gamma.ar:    0.945 
Score segment:      1.563 

--- K = 5 ---
Median Z.ar:        0.4588889 
Median Beta.ar:     1 
Median Gamma.ar:    0.4433333 
Score segment:      1.200222 

--- K = 6 ---
Median Z.ar:        0.3966667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3638889 
Score segment:      1.058556 

--- K = 7 ---
Median Z.ar:        0.405 
Median Beta.ar:     1 
Median Gamma.ar:    0.2188889 
Score segment:      0.9521111 

--- K = 8 ---
Median Z.ar:        0.5266667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.292667 

--- K = 9 ---
Median Z.ar:        0.7788889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.544889 

## Final Score
Final Score: 12.54656 
', '\n```'))
```
