---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 1.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8477778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3688889 
Score segment:      1.514667 

--- K = 2 ---
Median Z.ar:        0.7644444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      2.062444 

--- K = 3 ---
Median Z.ar:        0.6877778 
Median Beta.ar:     1 
Median Gamma.ar:    0.8672222 
Score segment:      1.853 

--- K = 4 ---
Median Z.ar:        0.6644444 
Median Beta.ar:     1 
Median Gamma.ar:    0.4533333 
Score segment:      1.415778 

--- K = 5 ---
Median Z.ar:        0.9644444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.730444 

--- K = 6 ---
Median Z.ar:        0.9811111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.747111 

--- K = 7 ---
Median Z.ar:        0.9838889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.749889 

--- K = 8 ---
Median Z.ar:        0.9627778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.728778 

--- K = 9 ---
Median Z.ar:        0.9866667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.752667 

## Final Score
Final Score: 15.55478 
', '\n```'))
```
