---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 1.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6 
Median Beta.ar:     1 
Median Gamma.ar:    0.3805556 
Score segment:      1.278556 

--- K = 2 ---
Median Z.ar:        0.3266667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.624667 

--- K = 3 ---
Median Z.ar:        0.2194444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.546556 

--- K = 4 ---
Median Z.ar:        0.1133333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.652667 

--- K = 5 ---
Median Z.ar:        0.1216667 
Median Beta.ar:     1 
Median Gamma.ar:    0.9438889 
Score segment:      1.588222 

--- K = 6 ---
Median Z.ar:        0.06666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.9438889 
Score segment:      1.643222 

--- K = 7 ---
Median Z.ar:        0.1055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.6222222 
Score segment:      1.282667 

--- K = 8 ---
Median Z.ar:        0.1561111 
Median Beta.ar:     1 
Median Gamma.ar:    0.4388889 
Score segment:      1.048778 

--- K = 9 ---
Median Z.ar:        0.1633333 
Median Beta.ar:     1 
Median Gamma.ar:    0.4261111 
Score segment:      1.028778 

## Final Score
Final Score: 12.69411 
', '\n```'))
```
