---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 1.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3816667 
Score segment:      1.118556 

--- K = 2 ---
Median Z.ar:        0.2116667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.554333 

--- K = 3 ---
Median Z.ar:        0.06111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.704889 

--- K = 4 ---
Median Z.ar:        0.03555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.730444 

--- K = 5 ---
Median Z.ar:        0.02888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.737111 

--- K = 6 ---
Median Z.ar:        0.02111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.744889 

--- K = 7 ---
Median Z.ar:        0.05277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6438889 
Score segment:      1.357111 

--- K = 8 ---
Median Z.ar:        0.04222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.5766667 
Score segment:      1.300444 

--- K = 9 ---
Median Z.ar:        0.04 
Median Beta.ar:     1 
Median Gamma.ar:    0.2761111 
Score segment:      1.002111 

## Final Score
Final Score: 13.24989 
', '\n```'))
```
