---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8477778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3738889 
Score segment:      1.519667 

--- K = 2 ---
Median Z.ar:        0.7611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      2.059111 

--- K = 3 ---
Median Z.ar:        0.6766667 
Median Beta.ar:     1 
Median Gamma.ar:    0.8833333 
Score segment:      1.858 

--- K = 4 ---
Median Z.ar:        0.6538889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3783333 
Score segment:      1.330222 

--- K = 5 ---
Median Z.ar:        0.6894444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.455444 

--- K = 6 ---
Median Z.ar:        0.7094444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.475444 

--- K = 7 ---
Median Z.ar:        0.7622222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.528222 

--- K = 8 ---
Median Z.ar:        0.905 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.671 

--- K = 9 ---
Median Z.ar:        0.9405556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.706556 

## Final Score
Final Score: 14.60367 
', '\n```'))
```
