---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.3772222 
Score segment:      1.388556 

--- K = 2 ---
Median Z.ar:        0.4916667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.789667 

--- K = 3 ---
Median Z.ar:        0.4338889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.731889 

--- K = 4 ---
Median Z.ar:        0.6638889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3311111 
Score segment:      1.293 

--- K = 5 ---
Median Z.ar:        0.4405556 
Median Beta.ar:     1 
Median Gamma.ar:    0.4216667 
Score segment:      1.160222 

--- K = 6 ---
Median Z.ar:        0.3133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.5072222 
Score segment:      1.118556 

--- K = 7 ---
Median Z.ar:        0.3566667 
Median Beta.ar:     1 
Median Gamma.ar:    0.27 
Score segment:      0.9246667 

--- K = 8 ---
Median Z.ar:        0.5811111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.347111 

--- K = 9 ---
Median Z.ar:        0.9016667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.667667 

## Final Score
Final Score: 12.42133 
', '\n```'))
```
