---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.715 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.216667 

--- K = 2 ---
Median Z.ar:        0.6061111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.256111 

--- K = 3 ---
Median Z.ar:        0.4922222 
Median Beta.ar:     1 
Median Gamma.ar:    0.86 
Score segment:      1.002222 

--- K = 4 ---
Median Z.ar:        0.7027778 
Median Beta.ar:     1 
Median Gamma.ar:    0.1466667 
Score segment:      1.106111 

--- K = 5 ---
Median Z.ar:        0.9838889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.533889 

--- K = 6 ---
Median Z.ar:        0.4633333 
Median Beta.ar:     1 
Median Gamma.ar:    0.08944444 
Score segment:      0.9238889 

--- K = 7 ---
Median Z.ar:        0.5261111 
Median Beta.ar:     1 
Median Gamma.ar:    0.005555556 
Score segment:      1.070556 

--- K = 8 ---
Median Z.ar:        0.92 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.47 

--- K = 9 ---
Median Z.ar:        0.9861111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.536111 

## Final Score
Final Score: 11.11556 
', '\n```'))
```
