---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7116667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3772222 
Score segment:      1.386889 

--- K = 2 ---
Median Z.ar:        0.5022222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.800222 

--- K = 3 ---
Median Z.ar:        0.4494444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.747444 

--- K = 4 ---
Median Z.ar:        0.3972222 
Median Beta.ar:     1 
Median Gamma.ar:    0.9283333 
Score segment:      1.623556 

--- K = 5 ---
Median Z.ar:        0.3783333 
Median Beta.ar:     1 
Median Gamma.ar:    0.575 
Score segment:      1.251333 

--- K = 6 ---
Median Z.ar:        0.34 
Median Beta.ar:     1 
Median Gamma.ar:    0.4661111 
Score segment:      1.104111 

--- K = 7 ---
Median Z.ar:        0.38 
Median Beta.ar:     1 
Median Gamma.ar:    0.2844444 
Score segment:      0.9624444 

--- K = 8 ---
Median Z.ar:        0.8872222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.653222 

--- K = 9 ---
Median Z.ar:        0.8855556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.651556 

## Final Score
Final Score: 13.18078 
', '\n```'))
```
