---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6005556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3788889 
Score segment:      1.277444 

--- K = 2 ---
Median Z.ar:        0.3377778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.635778 

--- K = 3 ---
Median Z.ar:        0.185 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.581 

--- K = 4 ---
Median Z.ar:        0.1172222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.648778 

--- K = 5 ---
Median Z.ar:        0.09888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.9838889 
Score segment:      1.651 

--- K = 6 ---
Median Z.ar:        0.09055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8683333 
Score segment:      1.543778 

--- K = 7 ---
Median Z.ar:        0.1077778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6738889 
Score segment:      1.332111 

--- K = 8 ---
Median Z.ar:        0.2505556 
Median Beta.ar:     1 
Median Gamma.ar:    0.2966667 
Score segment:      0.8452222 

--- K = 9 ---
Median Z.ar:        0.1611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.4044444 
Score segment:      1.009333 

## Final Score
Final Score: 12.52444 
', '\n```'))
```
