---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.8\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6033333 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.104444 

--- K = 2 ---
Median Z.ar:        0.3861111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.163889 

--- K = 3 ---
Median Z.ar:        0.165 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.385 

--- K = 4 ---
Median Z.ar:        0.2294444 
Median Beta.ar:     1 
Median Gamma.ar:    0.8605556 
Score segment:      1.181111 

--- K = 5 ---
Median Z.ar:        0.1266667 
Median Beta.ar:     1 
Median Gamma.ar:    0.8827778 
Score segment:      1.306111 

--- K = 6 ---
Median Z.ar:        0.1288889 
Median Beta.ar:     1 
Median Gamma.ar:    0.69 
Score segment:      1.111111 

--- K = 7 ---
Median Z.ar:        0.1955556 
Median Beta.ar:     1 
Median Gamma.ar:    0.2683333 
Score segment:      0.9861111 

--- K = 8 ---
Median Z.ar:        0.1944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3088889 
Score segment:      0.9466667 

--- K = 9 ---
Median Z.ar:        0.6566667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.206667 

## Final Score
Final Score: 10.39111 
', '\n```'))
```
