---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.385 
Median Beta.ar:     1 
Median Gamma.ar:    0.3811111 
Score segment:      1.064111 

--- K = 2 ---
Median Z.ar:        0.1311111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.634889 

--- K = 3 ---
Median Z.ar:        0.04333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.722667 

--- K = 4 ---
Median Z.ar:        0.02944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.736556 

--- K = 5 ---
Median Z.ar:        0.02555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.740444 

--- K = 6 ---
Median Z.ar:        0.01333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.752667 

--- K = 7 ---
Median Z.ar:        0.01055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.755444 

--- K = 8 ---
Median Z.ar:        0.01833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6405556 
Score segment:      1.388222 

--- K = 9 ---
Median Z.ar:        0.01722222 
Median Beta.ar:     1 
Median Gamma.ar:    0.5241667 
Score segment:      1.272944 

## Final Score
Final Score: 14.06794 
', '\n```'))
```
