---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3883333 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.012778 

--- K = 2 ---
Median Z.ar:        0.1361111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.413889 

--- K = 3 ---
Median Z.ar:        0.05055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.499444 

--- K = 4 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.525 

--- K = 5 ---
Median Z.ar:        0.02555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.524444 

--- K = 6 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.530556 

--- K = 7 ---
Median Z.ar:        0.02444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.8538889 
Score segment:      1.379444 

--- K = 8 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.6577778 
Score segment:      1.188333 

--- K = 9 ---
Median Z.ar:        0.02333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.5961111 
Score segment:      1.122778 

## Final Score
Final Score: 12.19667 
', '\n```'))
```
