---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3838889 
Median Beta.ar:     1 
Median Gamma.ar:    0.3822222 
Score segment:      1.064111 

--- K = 2 ---
Median Z.ar:        0.1322222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.633778 

--- K = 3 ---
Median Z.ar:        0.03722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.728778 

--- K = 4 ---
Median Z.ar:        0.02277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.743222 

--- K = 5 ---
Median Z.ar:        0.02166667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.744333 

--- K = 6 ---
Median Z.ar:        0.02333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.742667 

--- K = 7 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.9405556 
Score segment:      1.687111 

--- K = 8 ---
Median Z.ar:        0.02277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6711111 
Score segment:      1.414333 

--- K = 9 ---
Median Z.ar:        0.01666667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3975 
Score segment:      1.146833 

## Final Score
Final Score: 13.90517 
', '\n```'))
```
