---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3877778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.013333 

--- K = 2 ---
Median Z.ar:        0.145 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.405 

--- K = 3 ---
Median Z.ar:        0.04444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.505556 

--- K = 4 ---
Median Z.ar:        0.02111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.528889 

--- K = 5 ---
Median Z.ar:        0.01833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.531667 

--- K = 6 ---
Median Z.ar:        0.02277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.9388889 
Score segment:      1.466111 

--- K = 7 ---
Median Z.ar:        0.01833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9194444 
Score segment:      1.451111 

--- K = 8 ---
Median Z.ar:        0.04111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.1766667 
Score segment:      1.232222 

--- K = 9 ---
Median Z.ar:        0.03111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.1675 
Score segment:      1.251389 

## Final Score
Final Score: 12.38528 
', '\n```'))
```
