---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2494444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3822222 
Score segment:      0.9296667 

--- K = 2 ---
Median Z.ar:        0.05833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.707667 

--- K = 3 ---
Median Z.ar:        0.01277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.753222 

--- K = 4 ---
Median Z.ar:        0.01388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.752111 

--- K = 5 ---
Median Z.ar:        0.01166667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.754333 

--- K = 6 ---
Median Z.ar:        0.01055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.755444 

--- K = 7 ---
Median Z.ar:        0.008888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.757111 

--- K = 8 ---
Median Z.ar:        0.005555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.7877778 
Score segment:      1.548222 

--- K = 9 ---
Median Z.ar:        0.008333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.1822222 
Score segment:      1.043444 

## Final Score
Final Score: 14.00122 
', '\n```'))
```
