---
title: "MultiOmicsSurvey Benchmark Function Documentation"
author: "MultiOmicsSurvey Project"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    highlight: tango
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: united
    highlight: tango
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{MultiOmicsSurvey}
  - \fancyhead[R]{Benchmark Function Documentation}
  - \usepackage{longtable}
  - \usepackage{booktabs}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Introduction

This document provides comprehensive documentation for all custom functions used in the performance benchmarking scripts of the MultiOmicsSurvey project. Functions are organized by source file location.

\newpage

# Utility Scripts (performance_jobs/)

## Create_feature_ranks.R

Script for creating feature rankings based on variance metrics for benchmarking perturbation experiments.

### rank_mad_ids

```{r}
rank_mad_ids <- function(mat) {
  stopifnot(!is.null(rownames(mat)))
  m <- apply(mat, 1, function(x) mad(x, na.rm = TRUE))
  keep <- which(!is.na(m))
  ord <- keep[order(m[keep], decreasing = TRUE)]
  rownames(mat)[ord]
}
```

**Description:** Ranks features (rows) of a matrix by their Median Absolute Deviation (MAD) in descending order. Used for continuous modalities (RNAseq, CNV, Methylation, miRNA).

| Parameter | Type | Description |
|-----------|------|-------------|
| `mat` | matrix | Feature-by-sample matrix with rownames as feature IDs |

**Returns:** Character vector of feature IDs ordered by decreasing MAD.

---

## Create_sample_subsets.R

Script for creating stratified sample subsets for benchmarking sample perturbation experiments.

### strat_sample_ids

```{r}
strat_sample_ids <- function(frac, B, er_factor_named) {
  ids_all <- names(er_factor_named)
  levs <- levels(er_factor_named)
  out <- vector("list", B)
  
  for (b in seq_len(B)) {
    picked <- character(0)
    for (lv in levs) {
      ids_lv <- ids_all[er_factor_named == lv]
      n_lv <- max(1L, round(length(ids_lv) * frac / 100))
      n_lv <- min(n_lv, length(ids_lv))
      picked <- c(picked, sample(ids_lv, size = n_lv, replace = FALSE))
    }
    out[[b]] <- picked
  }
  out
}
```

**Description:** Creates stratified random samples of sample IDs, maintaining the proportion of each stratum (e.g., ER status). Generates B replicate subsets at a given fraction.

| Parameter | Type | Description |
|-----------|------|-------------|
| `frac` | numeric | Percentage of samples to include (0-100) |
| `B` | integer | Number of replicate subsets to generate |
| `er_factor_named` | factor | Named factor with sample IDs as names and strata as levels |

**Returns:** List of length B, each element containing a character vector of sampled IDs.

\newpage

# Algorithm Benchmark Scripts

## ab-SNF

Source files: `ab-SNF_feature_experiments.R`, `ab-SNF_sample_experiments.R`

### get_top_features

```{r}
get_top_features <- function(feat_rank_dt, centile) {
  mods <- unique(feat_rank_dt$modality)
  out <- vector("list", length(mods)); names(out) <- mods
  for (mod in mods) {
    mod_dt <- feat_rank_dt[modality == mod][order(rank)]
    top_n <- max(1L, ceiling(centile * nrow(mod_dt)))
    out[[mod]] <- mod_dt$feature_id[seq_len(top_n)]
  }
  out
}
```

**Description:** Extracts the top-ranked features for each modality based on a centile threshold.

| Parameter | Type | Description |
|-----------|------|-------------|
| `feat_rank_dt` | data.table | Feature rankings with columns: modality, rank, feature_id |
| `centile` | numeric | Fraction of features to select (0-1) |

**Returns:** Named list of character vectors, one per modality, containing selected feature IDs.

---

### subset_input_features

```{r}
subset_input_features <- function(input_obj, top_features) {
  out <- input_obj
  for (mod in names(top_features)) {
    if (!is.null(out[[mod]])) {
      keep <- intersect(top_features[[mod]], rownames(out[[mod]]))
      out[[mod]] <- out[[mod]][keep, , drop = FALSE]
      if (nrow(out[[mod]]) == 0L) out[[mod]] <- NULL
    }
  }
  out
}
```

**Description:** Subsets an input object (list of matrices) to retain only specified features per modality.

| Parameter | Type | Description |
|-----------|------|-------------|
| `input_obj` | list | Named list of feature-by-sample matrices |
| `top_features` | list | Named list of feature IDs to retain per modality |

**Returns:** Modified input object with subsetted matrices.

---

### subset_input_cols

```{r}
subset_input_cols <- function(input_obj, keep_ids) {
  out <- input_obj
  for (nm in names(out)) {
    if (!is.null(out[[nm]])) {
      kk <- keep_ids[keep_ids %in% colnames(out[[nm]])]
      out[[nm]] <- out[[nm]][, kk, drop = FALSE]
      if (ncol(out[[nm]]) == 0L) out[[nm]] <- NULL
    }
  }
  out
}
```

**Description:** Subsets an input object (list of matrices) to retain only specified samples (columns).

| Parameter | Type | Description |
|-----------|------|-------------|
| `input_obj` | list | Named list of feature-by-sample matrices |
| `keep_ids` | character | Sample IDs to retain |

**Returns:** Modified input object with subsetted columns.

---

### mad_based_weights

```{r}
mad_based_weights <- function(X) {
  v <- apply(X, 2, mad, na.rm = TRUE)
  v[!is.finite(v)] <- 0
  s <- sum(v)
  if (s <= 0) rep(0, length(v)) else v / s
}
```

**Description:** Computes feature weights based on column-wise MAD values, normalized to sum to 1.

| Parameter | Type | Description |
|-----------|------|-------------|
| `X` | matrix | Sample-by-feature matrix |

**Returns:** Numeric vector of normalized weights.

---

### weighted_euclidean_dist

```{r}
weighted_euclidean_dist <- function(X, w, ids) {
  Xw <- sweep(X, 2, sqrt(w), `*`)
  d <- abSNF::dist2(as.matrix(Xw), as.matrix(Xw))
  dimnames(d) <- list(ids, ids)
  d
}
```

**Description:** Computes weighted Euclidean distance matrix using feature weights.

| Parameter | Type | Description |
|-----------|------|-------------|
| `X` | matrix | Sample-by-feature data matrix |
| `w` | numeric | Feature weights |
| `ids` | character | Sample identifiers for row/column names |

**Returns:** Square distance matrix with sample IDs as dimnames.

---

### weighted_hamming_fraction_fast

```{r}
weighted_hamming_fraction_fast <- function(Xbin, features, drivers, 
                                           driver_w = 0.8, nondriver_w = 0.2, ids) {
  X <- (as.matrix(Xbin) != 0) * 1
  w <- ifelse(features %in% drivers, driver_w, nondriver_w)
  w[!is.finite(w)] <- 0
  total_w <- sum(w)
  if (total_w <= 0) {
    d <- matrix(0, nrow = nrow(X), ncol = nrow(X))
    dimnames(d) <- list(ids, ids)
    return(d)
  }
  Xw <- sweep(X, 2, sqrt(w), `*`)
  C <- Xw %*% t(Xw)
  s <- as.numeric(X %*% w)
  d <- outer(s, s, "+") - 2 * C
  d <- pmax(d, 0)
  d <- d / total_w
  dimnames(d) <- list(ids, ids)
  d
}
```

**Description:** Computes weighted Hamming distance for binary data, with higher weights for driver genes.

| Parameter | Type | Description |
|-----------|------|-------------|
| `Xbin` | matrix | Binary sample-by-feature matrix |
| `features` | character | Feature names (column names) |
| `drivers` | character | Driver gene names to upweight |
| `driver_w` | numeric | Weight for driver features (default: 0.8) |
| `nondriver_w` | numeric | Weight for non-driver features (default: 0.2) |
| `ids` | character | Sample identifiers |

**Returns:** Square distance matrix with sample IDs as dimnames.

---

### spectralClustering_eig

```{r}
spectralClustering_eig <- function(affinity, K, type = 3) {
  ids <- colnames(affinity) %||% rownames(affinity) %||% paste0("S", seq_len(nrow(affinity)))
  
  d <- rowSums(affinity)
  d[d == 0] <- .Machine$double.eps
  D <- diag(d)
  L <- D - affinity
  if (type == 1) {
    NL <- L
  } else if (type == 2) {
    NL <- diag(1 / d) %*% L
  } else {
    Di <- diag(1 / sqrt(d))
    NL <- Di %*% L %*% Di
  }
  
  eig <- eigen(NL)
  res <- sort(abs(eig$values), index.return = TRUE)
  U <- eig$vectors[, res$ix[1:K], drop = FALSE]
  
  if (type == 3) {
    normalize <- function(x) x / sqrt(sum(x^2))
    U <- t(apply(U, 1, normalize))
  }
  
  eigDiscrete <- SNFtool:::.discretisation(U)$discrete
  labels <- apply(eigDiscrete, 1, which.max)
  
  out <- as.data.frame(U)
  out$Cluster <- labels
  out$Sample.ID <- ids
  out
}
```

**Description:** Performs spectral clustering on an affinity matrix using eigendecomposition of the graph Laplacian.

| Parameter | Type | Description |
|-----------|------|-------------|
| `affinity` | matrix | Square affinity/similarity matrix |
| `K` | integer | Number of clusters |
| `type` | integer | Laplacian type: 1=unnormalized, 2=random walk, 3=symmetric (default) |

**Returns:** Data frame with eigenvector embeddings, cluster assignments, and sample IDs.

---

### ari_to_ground_truth

```{r}
ari_to_ground_truth <- function(gt_df, pred_df) {
  merged <- merge(gt_df, pred_df, by = "Sample.ID")
  if (nrow(merged) == 0) return(NA_real_)
  adjustedRandIndex(merged[["Cluster_gt"]], merged[["Cluster_pred"]])
}
```

**Description:** Computes Adjusted Rand Index between predicted clusters and ground truth labels.

| Parameter | Type | Description |
|-----------|------|-------------|
| `gt_df` | data.frame | Ground truth with columns: Sample.ID, Cluster_gt |
| `pred_df` | data.frame | Predictions with columns: Sample.ID, Cluster_pred |

**Returns:** Numeric ARI value, or NA if no samples match.

---

### get_int1

```{r}
get_int1 <- function(x) {
  if (is.null(x) || length(x) == 0L || is.na(x)) NA_integer_ else as.integer(x[1])
}
```

**Description:** Safely extracts the first element as integer, returning NA for NULL/empty/NA inputs.

| Parameter | Type | Description |
|-----------|------|-------------|
| `x` | any | Input value |

**Returns:** Integer or NA_integer_.

\newpage

## ANF

Source files: `ANF_feature_experiments.R`, `ANF_sample_experiments.R`

*Note: ANF scripts share many functions with ab-SNF (get_top_features, subset_input_features, spectralClustering_eig, ari_to_ground_truth). The ANF scripts use the same helper functions but call `ANF::affinity_matrix()` and `ANF::ANF()` for network fusion instead of SNF.*

\newpage

## CIMLR

Source files: `CIMLR_feature_experiments.R`, `CIMLR_sample_experiments.R`

*Note: CIMLR scripts share get_top_features, subset_input_features, subset_input_cols, ari_to_ground_truth with other algorithms.*

### extract_m3c_scores

```{r}
extract_m3c_scores <- function(m3c_obj, k = 2L) {
  sc <- m3c_obj$scores
  if (is.null(sc)) return(list(p = NA_real_, entropy = NA_real_, rcsi = NA_real_))
  sc <- as.data.frame(sc)
  row <- if ("K" %in% colnames(sc)) sc[sc$K == k, , drop = FALSE] else sc[k - 1L, , drop = FALSE]
  if (nrow(row) == 0) row <- sc[1, , drop = FALSE]

  p_col <- if ("NORM_P" %in% colnames(row)) "NORM_P" 
           else if ("MONTECARLO_P" %in% colnames(row)) "MONTECARLO_P" 
           else if ("BETA_P" %in% colnames(row)) "BETA_P" else NA_character_
  e_col <- if ("Entropy" %in% colnames(row)) "Entropy" else {
    cand <- grep("entropy", colnames(row), ignore.case = TRUE, value = TRUE)
    if (length(cand)) cand[1] else NA_character_
  }
  r_col <- if ("RCSI" %in% colnames(row)) "RCSI" else {
    cand <- grep("^RCSI", colnames(row), value = TRUE)
    if (length(cand)) cand[1] else NA_character_
  }

  list(
    p = if (!is.na(p_col)) as.numeric(row[[p_col]][1]) else NA_real_,
    entropy = if (!is.na(e_col)) as.numeric(row[[e_col]][1]) else NA_real_,
    rcsi = if (!is.na(r_col)) as.numeric(row[[r_col]][1]) else NA_real_
  )
}
```

**Description:** Extracts M3C consensus clustering scores for a specified number of clusters.

| Parameter | Type | Description |
|-----------|------|-------------|
| `m3c_obj` | list | M3C result object |
| `k` | integer | Number of clusters to extract scores for |

**Returns:** Named list with p-value, entropy, and RCSI scores.

---

### extract_m3c_clusters

```{r}
extract_m3c_clusters <- function(m3c_obj, k = 2L) {
  if (!is.null(m3c_obj$realdataresults) && length(m3c_obj$realdataresults) >= k) {
    ann <- m3c_obj$realdataresults[[k]]$ordered_annotation
    if (!is.null(ann) && "consensuscluster" %in% colnames(ann)) {
      ids <- if ("ID" %in% colnames(ann)) ann$ID else rownames(ann)
      return(data.frame(Sample.ID = ids, Cluster_pred = as.integer(ann$consensuscluster)))
    }
  }
  NULL
}
```

**Description:** Extracts consensus cluster assignments from an M3C result object.

| Parameter | Type | Description |
|-----------|------|-------------|
| `m3c_obj` | list | M3C result object |
| `k` | integer | Number of clusters |

**Returns:** Data frame with Sample.ID and Cluster_pred columns, or NULL if unavailable.

\newpage

## COCA

Source files: `COCA_feature_experiments.R`, `COCA_sample_experiments.R`

*Note: COCA scripts share get_top_features, subset_input_features, subset_input_cols, ari_to_ground_truth with other algorithms.*

### coca_distances_for

```{r}
coca_distances_for <- function(mod_names) {
  vapply(mod_names, function(m) if (identical(m, "SNPs")) "binary" else "euclidean", character(1))
}
```

**Description:** Assigns appropriate distance metric for each modality (binary for SNPs, euclidean for others).

| Parameter | Type | Description |
|-----------|------|-------------|
| `mod_names` | character | Vector of modality names |

**Returns:** Named character vector of distance metrics.

---

### to_samples_x_features

```{r}
to_samples_x_features <- function(mat) {
  stopifnot(!is.null(rownames(mat)), !is.null(colnames(mat)))
  t(as.matrix(mat))
}
```

**Description:** Transposes a feature-by-sample matrix to sample-by-feature format required by COCA.

| Parameter | Type | Description |
|-----------|------|-------------|
| `mat` | matrix | Feature-by-sample matrix with dimnames |

**Returns:** Transposed matrix (samples as rows, features as columns).

---

### align_by_samples

```{r}
align_by_samples <- function(X_list) {
  ids_list <- lapply(X_list, rownames)
  common <- Reduce(intersect, ids_list)
  if (length(common) == 0) stop("No common sample IDs across modalities after transpose.")
  common <- common[common %in% ids_list[[1]]]
  lapply(X_list, function(m) m[common, , drop = FALSE])
}
```

**Description:** Aligns a list of sample-by-feature matrices to common samples across all modalities.

| Parameter | Type | Description |
|-----------|------|-------------|
| `X_list` | list | Named list of sample-by-feature matrices |

**Returns:** List of matrices with identical rownames (samples).

\newpage

## iClusterBayes

Source files: `iClusterBayes_feature_experiments.R`, `iClusterBayes_sample_experiments.R`

*Note: iClusterBayes scripts share get_top_features, subset_input_features, subset_input_cols with other algorithms.*

### with_install_lock

```{r}
with_install_lock <- function(expr) {
  lockdir <- file.path(user_lib, ".pkg_install_lockdir")
  repeat {
    if (dir.create(lockdir, showWarnings = FALSE)) break
    Sys.sleep(2)
  }
  on.exit(unlink(lockdir, recursive = TRUE, force = TRUE), add = TRUE)
  force(expr)
}
```

**Description:** Executes an expression with a directory-based lock to prevent concurrent package installations in HPC array jobs.

| Parameter | Type | Description |
|-----------|------|-------------|
| `expr` | expression | Expression to evaluate under lock |

**Returns:** Result of the evaluated expression.

---

### ensure_cran_pkg

```{r}
ensure_cran_pkg <- function(pkg) {
  if (requireNamespace(pkg, quietly = TRUE)) return(invisible(TRUE))
  with_install_lock({
    install.packages(pkg, lib = user_lib, repos = "https://cran.r-project.org")
  })
  if (!requireNamespace(pkg, quietly = TRUE)) stop("Failed to install CRAN package: ", pkg)
  invisible(TRUE)
}
```

**Description:** Ensures a CRAN package is installed, using installation locking for HPC safety.

| Parameter | Type | Description |
|-----------|------|-------------|
| `pkg` | character | Package name |

**Returns:** Invisible TRUE on success; stops on failure.

---

### ensure_bioc_pkg

```{r}
ensure_bioc_pkg <- function(pkg) {
  ensure_cran_pkg("BiocManager")
  if (requireNamespace(pkg, quietly = TRUE)) return(invisible(TRUE))
  with_install_lock({
    BiocManager::install(pkg, lib = user_lib, ask = FALSE, update = FALSE)
  })
  if (!requireNamespace(pkg, quietly = TRUE)) stop("Failed to install Bioconductor package: ", pkg)
  invisible(TRUE)
}
```

**Description:** Ensures a Bioconductor package is installed, using installation locking for HPC safety.

| Parameter | Type | Description |
|-----------|------|-------------|
| `pkg` | character | Package name |

**Returns:** Invisible TRUE on success; stops on failure.

---

### align_modalities

```{r}
align_modalities <- function(X_list, ref_mod = NULL) {
  ids_list <- lapply(X_list, colnames)
  common <- Reduce(intersect, ids_list)
  if (length(common) == 0L) stop("No common sample IDs across modalities.")
  if (!is.null(ref_mod) && ref_mod %in% names(X_list)) {
    common <- common[common %in% colnames(X_list[[ref_mod]])]
  }
  lapply(X_list, function(m) m[, common, drop = FALSE])
}
```

**Description:** Aligns a list of feature-by-sample matrices to common samples across all modalities.

| Parameter | Type | Description |
|-----------|------|-------------|
| `X_list` | list | Named list of feature-by-sample matrices |
| `ref_mod` | character | Optional reference modality for ordering |

**Returns:** List of matrices with identical colnames (samples).

\newpage

# KLIC

Source files: `KLIC_feature_experiments.R`, `KLIC_sample_experiments.R`

*Note: KLIC scripts share get_top_features, subset_input_features, subset_input_cols, and ari_to_ground_truth with other algorithms.*

## ensure_mosek_env

```{r}
ensure_mosek_env <- function() {
  mosek_path <- Sys.getenv("MOSEK_PATH", "")
  if (mosek_path == "" || !dir.exists(mosek_path)) {
    stop("MOSEK_PATH not set or invalid. Set Sys.setenv(MOSEK_PATH = '/path/to/mosek').")
  }
  lic_dir <- file.path(mosek_path, "mosek")
  if (!file.exists(file.path(lic_dir, "mosek.lic"))) {
    stop("mosek.lic not found in expected location: ", lic_dir)
  }
  Sys.setenv(MOSEKLM_LICENSE_FILE = file.path(lic_dir, "mosek.lic"))
  invisible(TRUE)
}
```

**Description:** Ensures MOSEK environment is properly configured for KLIC optimization.

| Parameter | Type | Description |
|-----------|------|-------------|
| (none) | - | Function takes no parameters |

**Returns:** Invisible TRUE on success; stops on failure.

---

## ensure_rmosek

```{r}
ensure_rmosek <- function() {
  ensure_mosek_env()
  if (!requireNamespace("Rmosek", quietly = TRUE)) {
    mosek_r_dir <- file.path(Sys.getenv("MOSEK_PATH"), "10.2", "tools", "platform",
                              "linux64x86", "rmosek")
    if (!dir.exists(mosek_r_dir)) stop("Rmosek directory not found: ", mosek_r_dir)
    install.packages(file.path(mosek_r_dir, "Rmosek_10.2.0.tar.gz"),
                     repos = NULL, type = "source")
  }
  invisible(TRUE)
}
```

**Description:** Ensures the Rmosek package is installed for KLIC's convex optimization.

| Parameter | Type | Description |
|-----------|------|-------------|
| (none) | - | Function takes no parameters |

**Returns:** Invisible TRUE on success; stops on failure.

---

## to_sample_feature

```{r}
to_sample_feature <- function(X) {
  if (nrow(X) > ncol(X)) return(X)  # Already samples × features

  t(X)  # Transpose from features × samples
}
```

**Description:** Ensures matrix is in samples-by-features orientation for KLIC.

| Parameter | Type | Description |
|-----------|------|-------------|
| `X` | matrix | Input matrix to orient |

**Returns:** Matrix with samples as rows and features as columns.

---

## align_by_common_samples

```{r}
align_by_common_samples <- function(X_list) {
  ids_list <- lapply(X_list, rownames)
  common <- Reduce(intersect, ids_list)
  if (length(common) == 0L) stop("No common samples.")
  lapply(X_list, function(m) m[common, , drop = FALSE])
}
```

**Description:** Aligns multiple matrices by common sample IDs (row names).

| Parameter | Type | Description |
|-----------|------|-------------|
| `X_list` | list | List of samples-by-features matrices |

**Returns:** List of aligned matrices with identical row names.

\newpage

# LRAcluster

Source files: `LRAcluster_feature_experiments.R`, `LRAcluster_sample_experiments.R`

*Note: LRAcluster scripts share get_top_features, subset_input_features, subset_input_cols, ari_to_ground_truth, align_modalities, and extract_m3c_clusters with other algorithms.*

## types_by_mod

```{r}
types_by_mod <- function(mod_names) {
  type_map <- c(
    RNAseq = "gaussian",
    CNV = "gaussian",
    Methylation = "gaussian",
    miRNA = "gaussian",
    SNPs = "binary"
  )
  out <- type_map[mod_names]
  if (anyNA(out)) stop("Unknown modality name(s): ", paste(mod_names[is.na(out)], collapse = ", "))
  out
}
```

**Description:** Maps modality names to LRAcluster data types.

| Parameter | Type | Description |
|-----------|------|-------------|
| `mod_names` | character | Vector of modality names |

**Returns:** Named character vector of data types ("gaussian" or "binary").

\newpage

# MDICC

Source files: `MDICC_feature_experiments.R`, `MDICC_sample_experiments.R`

*Note: MDICC scripts share get_top_features, subset_input_features, subset_input_cols, ari_to_ground_truth, and to_sample_feature with other algorithms.*

## get_mdicc_field

```{r}
get_mdicc_field <- function(result, field, default = NULL) {
  if (is.null(result) || !is.list(result)) return(default)
  if (field %in% names(result)) return(result[[field]])
  default
}
```

**Description:** Safely extracts a field from MDICC result objects.

| Parameter | Type | Description |
|-----------|------|-------------|
| `result` | list | MDICC result object |
| `field` | character | Field name to extract |
| `default` | any | Default value if field not found |

**Returns:** Extracted field value or default.

---

## same_conda_prefix

```{r}
same_conda_prefix <- function(a, b) {
  normalizePath(a, winslash = "/", mustWork = FALSE) ==
    normalizePath(b, winslash = "/", mustWork = FALSE)
}
```

**Description:** Compares two paths to check if they refer to the same conda environment.

| Parameter | Type | Description |
|-----------|------|-------------|
| `a` | character | First path |
| `b` | character | Second path |

**Returns:** Logical TRUE if paths are equivalent.

---

## ensure_python

```{r}
ensure_python <- function(conda_env = "mdicc_env") {
  if (!reticulate::condaenv_exists(conda_env)) {
    stop("Conda environment not found: ", conda_env)
  }
  current <- tryCatch(reticulate::py_config()$prefix, error = function(e) "")
  target <- reticulate::conda_python(envname = conda_env)
  target_prefix <- dirname(dirname(target))
  if (!same_conda_prefix(current, target_prefix)) {
    reticulate::use_condaenv(conda_env, required = TRUE)
  }
  invisible(TRUE)
}
```

**Description:** Ensures the correct Python conda environment is active for MDICC.

| Parameter | Type | Description |
|-----------|------|-------------|
| `conda_env` | character | Conda environment name (default: "mdicc_env") |

**Returns:** Invisible TRUE on success; stops on failure.

---

## ensure_projsplx

```{r}
ensure_projsplx <- function() {
  py <- reticulate::import("sys")
  if (!reticulate::py_module_available("projsplx")) {
    reticulate::py_install("projsplx", pip = TRUE)
  }
  invisible(TRUE)
}
```

**Description:** Ensures the projsplx Python package is installed.

| Parameter | Type | Description |
|-----------|------|-------------|
| (none) | - | Function takes no parameters |

**Returns:** Invisible TRUE on success.

---

## fallback_testaff

```{r}
fallback_testaff <- function(data_list, k = 5L) {
  n <- nrow(data_list[[1]])
  affs <- lapply(data_list, function(X) {
    D <- as.matrix(dist(X))
    exp(-D^2 / (2 * median(D)^2))
  })
  Reduce(`+`, affs) / length(affs)
}
```

**Description:** Fallback affinity computation when MDICC Python call fails.

| Parameter | Type | Description |
|-----------|------|-------------|
| `data_list` | list | List of data matrices |
| `k` | integer | Number of neighbors (default: 5) |

**Returns:** Averaged affinity matrix.

---

## fallback_MDICClabel

```{r}
fallback_MDICClabel <- function(affinity, nclust) {
  km <- kmeans(affinity, centers = nclust, nstart = 25L)
  list(labels = km$cluster, converged = TRUE, obj = km$tot.withinss)
}
```

**Description:** Fallback clustering when MDICC label function fails.

| Parameter | Type | Description |
|-----------|------|-------------|
| `affinity` | matrix | Affinity matrix |
| `nclust` | integer | Number of clusters |

**Returns:** List with labels, convergence flag, and objective value.

\newpage

# MONET

Source files: `MONET_make_correlations_feature.R`, `MONET_make_correlations_sample.R`, `run_MONET_mainloop.py`

*Note: MONET R scripts share get_top_features, subset_input_features, and ari_to_ground_truth with other algorithms.*

## parse_args (MONET R) {#parse_args}

```{r}
parse_args <- function() {
  args <- commandArgs(trailingOnly = TRUE)
  if (length(args) < 2L) stop("Usage: Rscript script.R <input_dir> <output_dir>")
  list(input_dir = args[1], output_dir = args[2])
}
```

**Description:** Parses command-line arguments for MONET R scripts.

| Parameter | Type | Description |
|-----------|------|-------------|
| (none) | - | Reads from commandArgs |

**Returns:** List with input_dir and output_dir paths.

---

## align_common_samples (MONET) {#align_common_samples}

```{r}
align_common_samples <- function(X_list) {
  ids_list <- lapply(X_list, colnames)
  common <- Reduce(intersect, ids_list)
  if (length(common) == 0L) stop("No common samples.")
  lapply(X_list, function(m) m[, common, drop = FALSE])
}
```

**Description:** Aligns feature-by-sample matrices to common column names.

| Parameter | Type | Description |
|-----------|------|-------------|
| `X_list` | list | List of feature-by-sample matrices |

**Returns:** List of aligned matrices.

\newpage

# MSNE

Source files: `MSNE_feature_experiments.R`, `MSNE_sample_experiments.R`, `MSNE_run.py`

*Note: MSNE R scripts share get_top_features, subset_input_features, and ari_to_ground_truth with other algorithms.*

## parse_timev

```{r}
parse_timev <- function(timev_str) {
  parts <- strsplit(timev_str, ":")[[1]]
  if (length(parts) == 3L) {
    as.numeric(parts[1]) * 3600 + as.numeric(parts[2]) * 60 + as.numeric(parts[3])
  } else if (length(parts) == 2L) {
    as.numeric(parts[1]) * 60 + as.numeric(parts[2])
  } else {
    as.numeric(timev_str)
  }
}
```

**Description:** Parses time strings in HH:MM:SS or MM:SS format to seconds.

| Parameter | Type | Description |
|-----------|------|-------------|
| `timev_str` | character | Time string to parse |

**Returns:** Numeric time in seconds.

\newpage

# NEMO

Source files: `NEMO_feature_experiments.R`, `NEMO_sample_experiments.R`

*Note: NEMO scripts share get_top_features, subset_input_features, ari_to_ground_truth, spectralClustering_eig, and align_common_samples with other algorithms.*

\newpage

# RWR-F

Source files: `RWR-F_feature_experiments.R`, `RWR-F_sample_experiments.R`

*Note: RWR-F scripts share get_top_features, subset_input_features, and ari_to_ground_truth with other algorithms.*

## parse_args (RWR-F)

```{r}
parse_args <- function() {
  args <- commandArgs(trailingOnly = TRUE)
  if (length(args) < 3L) stop("Usage: Rscript script.R <input_rds> <output_dir> <n_clusters>")
  list(
    input_rds = args[1],
    output_dir = args[2],
    n_clusters = as.integer(args[3])
  )
}
```

**Description:** Parses command-line arguments for RWR-F scripts.

| Parameter | Type | Description |
|-----------|------|-------------|
| (none) | - | Reads from commandArgs |

**Returns:** List with input_rds, output_dir, and n_clusters.

---

## specc_with_embedding

```{r}
specc_with_embedding <- function(affinity, K) {
  n <- nrow(affinity)
  D_inv_sqrt <- diag(1 / sqrt(rowSums(affinity) + .Machine$double.eps))
  L_sym <- D_inv_sqrt %*% affinity %*% D_inv_sqrt
  eig <- eigen(L_sym, symmetric = TRUE)
  U <- eig$vectors[, seq_len(K), drop = FALSE]
  U_norm <- U / sqrt(rowSums(U^2) + .Machine$double.eps)
  km <- kmeans(U_norm, centers = K, nstart = 25L, iter.max = 100L)
  list(labels = km$cluster, embedding = U_norm)
}
```

**Description:** Performs spectral clustering on an affinity matrix, returning both labels and embedding.

| Parameter | Type | Description |
|-----------|------|-------------|
| `affinity` | matrix | Affinity/similarity matrix |
| `K` | integer | Number of clusters |

**Returns:** List with cluster labels and normalized eigenvector embedding.

\newpage

# SNF

Source files: `SNF_feature_experiments.R`, `SNF_sample_experiments.R`

*Note: SNF scripts share get_top_features, subset_input_features, ari_to_ground_truth, and spectralClustering_eig with other algorithms.*

\newpage

# Spectrum

Source files: `Spectrum_feature_experiments.R`, `Spectrum_sample_experiments.R`

*Note: Spectrum scripts share get_top_features, subset_input_features, and ari_to_ground_truth with other algorithms.*

## ref_modality

```{r}
ref_modality <- function(input_list, prefer = "RNAseq") {
  non_null <- names(input_list)[!vapply(input_list, is.null, logical(1))]
  if (length(non_null) == 0) stop("All modalities are NULL.")
  if (prefer %in% non_null) return(prefer)
  non_null[1]
}
```

**Description:** Selects a reference modality from an input list, preferring a specified modality if available.

| Parameter | Type | Description |
|-----------|------|-------------|
| `input_list` | list | Named list of modality matrices |
| `prefer` | character | Preferred modality name (default: "RNAseq") |

**Returns:** Name of the selected reference modality.

---

## safe_silhouette_avg

```{r}
safe_silhouette_avg <- function(assignments, embeddings) {
  cl <- as.integer(assignments)
  if (length(unique(cl)) < 2L || nrow(embeddings) < 3L) return(NA_real_)
  sil <- silhouette(cl, dist = Rfast::Dist(as.matrix(embeddings), method = "euclidean"))
  summary(sil)$avg.width
}
```

**Description:** Computes average silhouette width with validation for edge cases.

| Parameter | Type | Description |
|-----------|------|-------------|
| `assignments` | vector | Cluster assignments |
| `embeddings` | matrix | Sample embeddings for distance computation |

**Returns:** Numeric average silhouette width, or NA for invalid inputs.

\newpage

# wMKL

Source files: `wMKL_feature_experiments.R`, `wMKL_sample_experiments.R`

*Note: wMKL scripts share get_top_features, subset_input_features, ari_to_ground_truth, and mad_based_weights with other algorithms.*

## weighted_mutations

```{r}
weighted_mutations <- function(features, drivers, driver_weight = 0.8, nondriver_weight = 0.2) {
  w <- ifelse(features %in% drivers, driver_weight, nondriver_weight)
  w[!is.finite(w)] <- 0
  if (sum(w) == 0) w <- rep(1, length(w))
  w <- w / sum(w)
  names(w) <- features
  w
}
```

**Description:** Computes normalized weights for mutation features, upweighting driver genes.

| Parameter | Type | Description |
|-----------|------|-------------|
| `features` | character | Feature names |
| `drivers` | character | Driver gene names |
| `driver_weight` | numeric | Weight for driver features (default: 0.8) |
| `nondriver_weight` | numeric | Weight for non-driver features (default: 0.2) |

**Returns:** Named numeric vector of normalized weights.

---

## extract_eigenspace

```{r}
extract_eigenspace <- function(affinity, K, type = 3) {
  d <- rowSums(affinity)
  d[d == 0] <- .Machine$double.eps
  # ... (Laplacian computation and eigendecomposition)
  list(labels = labels, U = U, eigDiscrete = eigDiscrete)
}
```

**Description:** Extracts eigenspace representation and cluster labels from an affinity matrix.

| Parameter | Type | Description |
|-----------|------|-------------|
| `affinity` | matrix | Affinity/similarity matrix |
| `K` | integer | Number of clusters |
| `type` | integer | Laplacian type (1, 2, or 3) |

**Returns:** List with `labels` (cluster assignments), `U` (eigenvectors), and `eigDiscrete` (discretized assignments).

---

## safe_avg_sil

```{r}
safe_avg_sil <- function(labels, U) {
  cl <- as.integer(labels)
  if (length(unique(cl)) < 2L || nrow(U) < 3L) return(NA_real_)
  sil <- silhouette(cl, dist = Rfast::Dist(as.matrix(U), method = "euclidean"))
  summary(sil)$avg.width
}
```

**Description:** Computes average silhouette width from cluster labels and eigenvector embeddings.

| Parameter | Type | Description |
|-----------|------|-------------|
| `labels` | vector | Cluster assignments |
| `U` | matrix | Eigenvector embeddings |

**Returns:** Numeric average silhouette width, or NA for invalid inputs.

\newpage

# Python Scripts

## MONET (run_MONET_mainloop.py)

### set_seeds (Python) {#set_seeds}

```{python}
def set_seeds(seed: int) -> None:
    random.seed(seed)
    np.random.seed(seed)
```

**Description:** Sets random seeds for reproducibility in both Python's random module and NumPy.

| Parameter | Type | Description |
|-----------|------|-------------|
| `seed` | int | Random seed value |

---

### load_correlation_matrices

```{python}
def load_correlation_matrices(directory: str) -> dict[str, pd.DataFrame]:
    csv_files = sorted(glob.glob(os.path.join(directory, "*.csv")))
    if len(csv_files) != 5:
        raise ValueError(f"Expected 5 CSV files in {directory}, found {len(csv_files)}.")
    data: dict[str, pd.DataFrame] = {}
    for file_path in csv_files:
        omic_name = os.path.splitext(os.path.basename(file_path))[0]
        data[omic_name] = _load_one_csv(file_path)
    return data
```

**Description:** Loads correlation matrices from CSV files for all omics modalities.

| Parameter | Type | Description |
|-----------|------|-------------|
| `directory` | str | Directory containing correlation CSV files |

**Returns:** Dictionary mapping omic names to correlation DataFrames.

---

## MSNE (MSNE_run.py)

### set_seeds (MSNE Python)

```{python}
def set_seeds(seed: int) -> None:
    np.random.seed(seed)
    random.seed(seed)
```

**Description:** Sets random seeds for reproducibility.

| Parameter | Type | Description |
|-----------|------|-------------|
| `seed` | int | Random seed value |

---

### load_views_from_csv

```{python}
def load_views_from_csv(dists_dir: str) -> list[pd.DataFrame]:
    csvs = sorted(glob.glob(os.path.join(dists_dir, "*.csv")))
    if len(csvs) != 5:
        raise ValueError(f"Expected 5 distance CSVs in {dists_dir}, found {len(csvs)}")
    views = []
    for fp in csvs:
        df = pd.read_csv(fp, index_col=0)
        views.append(df)
    return views
```

**Description:** Loads distance matrices from CSV files as views for MSNE.

| Parameter | Type | Description |
|-----------|------|-------------|
| `dists_dir` | str | Directory containing distance CSV files |

**Returns:** List of DataFrames representing views.

\newpage

# Post-Analysis Scripts (automated_scripts/)

*These functions are used AFTER HPC benchmark runs to aggregate, visualize, and analyze results. They are not part of the algorithm execution itself.*

## benchmark_plotting_functions.R

Source file: `Scripts/automated_scripts/benchmark_plotting_functions.R`

This script provides comprehensive visualization and analysis functions for benchmark results. Key capabilities include:

- Reading and standardizing performance TSV files from various algorithm outputs
- Creating publication-ready plots for ARI, runtime, and memory metrics
- Fitting empirical time complexity models
- Computing stability metrics across replicate runs

### theme_benchmark

```{r}
theme_benchmark <- function(base_size = 10, legend = FALSE) {
  theme_bw(base_size = base_size) +
    theme(
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.line.x = element_line(color = "black"),
      axis.line.y = element_line(color = "black"),
      plot.title = element_text(face = "bold", hjust = 0.5),
      axis.title = element_text(face = "bold"),
      legend.position = if (isTRUE(legend)) "right" else "none",
      plot.margin = margin(5.5, 70, 5.5, 5.5, "pt")
    )
}
```

**Description:** Creates a clean, publication-ready ggplot2 theme with minimal gridlines and bold titles.

| Parameter | Type | Description |
|-----------|------|-------------|
| `base_size` | numeric | Base font size (default: 10) |
| `legend` | logical | If TRUE, legend on right; if FALSE, legend hidden |

**Returns:** A ggplot2 theme object.

---

### guess_benchmark_dirs

```{r}
guess_benchmark_dirs <- function(root = "Results/Performance_benchmarks")
```

**Description:** Locates the feature and sample perturbation directories within a benchmark results root. Handles common typos in directory names.

| Parameter | Type | Description |
|-----------|------|-------------|
| `root` | character | Path to benchmark results root directory |

**Returns:** Named list with `feature_dir` and `sample_dir` paths.

---

### read_mode_perf

```{r}
read_mode_perf <- function(mode = c("feature", "sample"),
                           root = "Results/Performance_benchmarks",
                           method_categories_map = method_categories)
```

**Description:** Discovers, reads, and standardizes all performance TSV files for either feature or sample perturbation experiments across all algorithms.

| Parameter | Type | Description |
|-----------|------|-------------|
| `mode` | character | Either "feature" or "sample" perturbation mode |
| `root` | character | Path to benchmark results root directory |
| `method_categories_map` | named vector | Mapping of algorithms to categories |

**Returns:** Aggregated data.table with standardized metrics per algorithm/subset combination.

---

### plot_metric_lines

```{r}
plot_metric_lines <- function(dt, mode, metric, x_axis, title, ylab, category_colors_map, legend)
```

**Description:** Generates a publication-ready line plot showing how a metric varies with subset size across algorithms.

| Parameter | Type | Description |
|-----------|------|-------------|
| `dt` | data.table | Aggregated data from `read_mode_perf` |
| `mode` | character | Either "feature" or "sample" |
| `metric` | character | One of "ARI_to_Ground_Truth", "Peak_MiB", or "Time_s" |
| `x_axis` | character | Either "percent" or "absolute" |
| `title` | character | Plot title |
| `ylab` | character | Y-axis label |
| `category_colors_map` | named vector | Category colors |
| `legend` | logical | Whether to show legend |

**Returns:** A ggplot object.

---

### save_plot_png_pdf

```{r}
save_plot_png_pdf <- function(p, title, out_dir, dpi = 700, width_px = 3840, height_px = 2160)
```

**Description:** Saves a ggplot object to both PNG and PDF formats with consistent naming and high resolution suitable for publication.

| Parameter | Type | Description |
|-----------|------|-------------|
| `p` | ggplot | Plot object to save |
| `title` | character | Title used to generate filename |
| `out_dir` | character | Output directory path |
| `dpi` | numeric | Dots per inch (default: 700) |
| `width_px` | numeric | Width in pixels (default: 3840 for 4K) |
| `height_px` | numeric | Height in pixels (default: 2160 for 4K) |

**Returns:** Invisible NULL.

---

### fit_time_scaling_models

```{r}
fit_time_scaling_models <- function(root = "Results/Performance_benchmarks",
                                    method_categories_map = method_categories,
                                    min_points = 4)
```

**Description:** Fits power-law models (T ~ size^k) to runtime data for both feature and sample perturbation modes across all algorithms. Returns estimated complexity in Big-O notation.

| Parameter | Type | Description |
|-----------|------|-------------|
| `root` | character | Path to benchmark results root directory |
| `method_categories_map` | named vector | Mapping of algorithms to categories |
| `min_points` | integer | Minimum data points for fitting (default: 4) |

**Returns:** Data.table with columns: Mode, Algorithm, Category, Predictor, Exponent, R2, O_notation.

---

### compute_sample_stability_90pct

```{r}
compute_sample_stability_90pct <- function(root = "Results/Performance_benchmarks",
                                           out_dir = "Results/Comparisons",
                                           pct = 90, min_common_sample = 20L,
                                           save = TRUE, dpi = 700,
                                           width_px = 3840, height_px = 2160)
```

**Description:** Analyzes replicate stability by computing pairwise ARI between clusterings at a target sample perturbation percentage. Creates violin plots and exports summary tables.

| Parameter | Type | Description |
|-----------|------|-------------|
| `root` | character | Path to benchmark results root directory |
| `out_dir` | character | Output directory for files |
| `pct` | numeric | Target perturbation percentage (default: 90) |
| `min_common_sample` | integer | Minimum common samples for ARI (default: 20) |
| `save` | logical | Whether to save plots and tables |

**Returns:** List with `pairs`, `summary`, `skipped`, and `plot` objects.

---

### make_benchmark_plots

```{r}
make_benchmark_plots <- function(root = "Results/Performance_benchmarks",
                                  out_dir = "Results/Comparisons",
                                  x_axis = c("percent", "absolute"),
                                  save = TRUE, dpi = 700,
                                  width_px = 3840, height_px = 2160,
                                  method_categories_map = method_categories,
                                  category_colors_map = category_colors,
                                  legend = FALSE)
```

**Description:** Main entry point for benchmark visualization. Reads performance data for both feature and sample perturbation experiments, generates line plots for ARI, runtime, and memory metrics, and optionally saves to disk.

| Parameter | Type | Description |
|-----------|------|-------------|
| `root` | character | Path to benchmark results root directory |
| `out_dir` | character | Output directory for files |
| `x_axis` | character | Either "percent" or "absolute" |
| `save` | logical | Whether to save plots (default: TRUE) |
| `method_categories_map` | named vector | Algorithm to category mapping |
| `category_colors_map` | named vector | Category color palette |
| `legend` | logical | Whether to show legend (default: FALSE) |

**Returns:** Invisible list of named plot objects with titles.

\newpage

# Alphabetical Index

| Function | Source File(s) |
|----------|---------------|
| [align_by_samples](#align_by_samples) | COCA |
| [align_common_samples](#align_common_samples) | MONET, NEMO |
| [align_modalities](#align_modalities) | iClusterBayes, LRAcluster |
| [ari_to_ground_truth](#ari_to_ground_truth) | ab-SNF, ANF, CIMLR, COCA, iClusterBayes, KLIC, LRAcluster, MDICC, NEMO, SNF, Spectrum, wMKL |
| [coca_distances_for](#coca_distances_for) | COCA |
| [compute_sample_stability_90pct](#compute_sample_stability_90pct) | benchmark_plotting_functions.R (Post-Analysis) |
| [ensure_bioc_pkg](#ensure_bioc_pkg) | iClusterBayes |
| [ensure_cran_pkg](#ensure_cran_pkg) | iClusterBayes |
| [ensure_mosek_env](#ensure_mosek_env) | KLIC |
| [ensure_projsplx](#ensure_projsplx) | MDICC |
| [ensure_python](#ensure_python) | MDICC |
| [ensure_rmosek](#ensure_rmosek) | KLIC |
| [extract_eigenspace](#extract_eigenspace) | wMKL |
| [extract_m3c_clusters](#extract_m3c_clusters) | CIMLR, LRAcluster |
| [extract_m3c_scores](#extract_m3c_scores) | CIMLR |
| [fallback_MDICClabel](#fallback_mdicclabel) | MDICC |
| [fallback_testaff](#fallback_testaff) | MDICC |
| [fit_time_scaling_models](#fit_time_scaling_models) | benchmark_plotting_functions.R (Post-Analysis) |
| [get_int1](#get_int1) | ab-SNF, COCA |
| [get_mdicc_field](#get_mdicc_field) | MDICC |
| [get_top_features](#get_top_features) | ab-SNF, ANF, CIMLR, COCA, iClusterBayes, KLIC, LRAcluster, MDICC, MONET, MSNE, NEMO, RWR-F, SNF, Spectrum, wMKL |
| [guess_benchmark_dirs](#guess_benchmark_dirs) | benchmark_plotting_functions.R (Post-Analysis) |
| [load_correlation_matrices](#load_correlation_matrices) | MONET (Python) |
| [load_views_from_csv](#load_views_from_csv) | MSNE (Python) |
| [mad_based_weights](#mad_based_weights) | ab-SNF, wMKL |
| [make_benchmark_plots](#make_benchmark_plots) | benchmark_plotting_functions.R (Post-Analysis) |
| [parse_args](#parse_args) | RWR-F |
| [parse_timev](#parse_timev) | MSNE |
| [plot_metric_lines](#plot_metric_lines) | benchmark_plotting_functions.R (Post-Analysis) |
| [rank_mad_ids](#rank_mad_ids) | Create_feature_ranks.R |
| [read_mode_perf](#read_mode_perf) | benchmark_plotting_functions.R (Post-Analysis) |
| [ref_modality](#ref_modality) | Spectrum |
| [safe_avg_sil](#safe_avg_sil) | wMKL |
| [safe_silhouette_avg](#safe_silhouette_avg) | Spectrum |
| [save_plot_png_pdf](#save_plot_png_pdf) | benchmark_plotting_functions.R (Post-Analysis) |
| [same_conda_prefix](#same_conda_prefix) | MDICC |
| [set_seeds](#set_seeds) | MONET (Python), MSNE (Python) |
| [specc_with_embedding](#specc_with_embedding) | RWR-F |
| [spectralClustering_eig](#spectralclustering_eig) | ab-SNF, ANF, NEMO, SNF |
| [strat_sample_ids](#strat_sample_ids) | Create_sample_subsets.R |
| [subset_input_cols](#subset_input_cols) | ab-SNF, CIMLR, COCA, iClusterBayes, KLIC, LRAcluster, MDICC |
| [subset_input_features](#subset_input_features) | ab-SNF, ANF, CIMLR, COCA, iClusterBayes, KLIC, LRAcluster, MDICC, MONET, MSNE, NEMO, RWR-F, SNF, Spectrum, wMKL |
| [theme_benchmark](#theme_benchmark) | benchmark_plotting_functions.R (Post-Analysis) |
| [to_sample_feature](#to_sample_feature) | KLIC, MDICC |
| [to_samples_x_features](#to_samples_x_features) | COCA |
| [types_by_mod](#types_by_mod) | LRAcluster |
| [weighted_euclidean_dist](#weighted_euclidean_dist) | ab-SNF |
| [weighted_hamming_fraction_fast](#weighted_hamming_fraction_fast) | ab-SNF |
| [weighted_mutations](#weighted_mutations) | wMKL |
| [with_install_lock](#with_install_lock) | iClusterBayes |
