---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5094444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3813889 
Score segment:      1.188833 

--- K = 2 ---
Median Z.ar:        0.2405556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.538556 

--- K = 3 ---
Median Z.ar:        0.1061111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.659889 

--- K = 4 ---
Median Z.ar:        0.07777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.688222 

--- K = 5 ---
Median Z.ar:        0.06722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.698778 

--- K = 6 ---
Median Z.ar:        0.05444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.9866667 
Score segment:      1.698222 

--- K = 7 ---
Median Z.ar:        0.05611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.7416667 
Score segment:      1.451556 

--- K = 8 ---
Median Z.ar:        0.07055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.4322222 
Score segment:      1.127667 

--- K = 9 ---
Median Z.ar:        0.05555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.465 
Score segment:      1.175444 

## Final Score
Final Score: 13.22717 
', '\n```'))
```
