---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.4\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5138889 
Median Beta.ar:     1 
Median Gamma.ar:    0.04944444 
Score segment:      1.014444 

--- K = 2 ---
Median Z.ar:        0.2427778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.307222 

--- K = 3 ---
Median Z.ar:        0.1605556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.389444 

--- K = 4 ---
Median Z.ar:        0.06833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.481667 

--- K = 5 ---
Median Z.ar:        0.05611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.493889 

--- K = 6 ---
Median Z.ar:        0.06888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.7944444 
Score segment:      1.275556 

--- K = 7 ---
Median Z.ar:        0.2622222 
Median Beta.ar:     1 
Median Gamma.ar:    0.1011111 
Score segment:      1.086667 

--- K = 8 ---
Median Z.ar:        0.8477778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.397778 

--- K = 9 ---
Median Z.ar:        0.1611111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.288889 

## Final Score
Final Score: 11.73556 
', '\n```'))
```
