---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8466667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3777778 
Score segment:      1.522444 

--- K = 2 ---
Median Z.ar:        0.7566667 
Median Beta.ar:     1 
Median Gamma.ar:    0.9627778 
Score segment:      2.017444 

--- K = 3 ---
Median Z.ar:        0.6605556 
Median Beta.ar:     1 
Median Gamma.ar:    0.655 
Score segment:      1.613556 

--- K = 4 ---
Median Z.ar:        0.6644444 
Median Beta.ar:     1 
Median Gamma.ar:    0.335 
Score segment:      1.297444 

--- K = 5 ---
Median Z.ar:        0.6933333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.459333 

--- K = 6 ---
Median Z.ar:        0.7361111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.502111 

--- K = 7 ---
Median Z.ar:        0.9038889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.669889 

--- K = 8 ---
Median Z.ar:        0.8333333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.599333 

--- K = 9 ---
Median Z.ar:        0.9377778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.703778 

## Final Score
Final Score: 14.38533 
', '\n```'))
```
