---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 1.25\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5994444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3805556 
Score segment:      1.278 

--- K = 2 ---
Median Z.ar:        0.3344444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.632444 

--- K = 3 ---
Median Z.ar:        0.1844444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.581556 

--- K = 4 ---
Median Z.ar:        0.1383333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.627667 

--- K = 5 ---
Median Z.ar:        0.1133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.9722222 
Score segment:      1.624889 

--- K = 6 ---
Median Z.ar:        0.09444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.8483333 
Score segment:      1.519889 

--- K = 7 ---
Median Z.ar:        0.2811111 
Median Beta.ar:     1 
Median Gamma.ar:    0.3866667 
Score segment:      0.9657778 

--- K = 8 ---
Median Z.ar:        0.5372222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.303222 

--- K = 9 ---
Median Z.ar:        0.3116667 
Median Beta.ar:     1 
Median Gamma.ar:    0.1533333 
Score segment:      0.9243333 

## Final Score
Final Score: 12.45778 
', '\n```'))
```
