---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4438889 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      0.9577778 

--- K = 2 ---
Median Z.ar:        0.1772222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.372778 

--- K = 3 ---
Median Z.ar:        0.09166667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.458333 

--- K = 4 ---
Median Z.ar:        0.04388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.506111 

--- K = 5 ---
Median Z.ar:        0.04555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.504444 

--- K = 6 ---
Median Z.ar:        0.02888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.521111 

--- K = 7 ---
Median Z.ar:        0.02055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8538889 
Score segment:      1.383333 

--- K = 8 ---
Median Z.ar:        0.05888889 
Median Beta.ar:     1 
Median Gamma.ar:    0.38 
Score segment:      1.011111 

--- K = 9 ---
Median Z.ar:        0.3283333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.121667 

## Final Score
Final Score: 11.83667 
', '\n```'))
```
