---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.44 
Median Beta.ar:     1 
Median Gamma.ar:    0.3816667 
Score segment:      1.119667 

--- K = 2 ---
Median Z.ar:        0.175 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.591 

--- K = 3 ---
Median Z.ar:        0.06555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.700444 

--- K = 4 ---
Median Z.ar:        0.05055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.715444 

--- K = 5 ---
Median Z.ar:        0.04166667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.724333 

--- K = 6 ---
Median Z.ar:        0.02611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.739889 

--- K = 7 ---
Median Z.ar:        0.03055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8411111 
Score segment:      1.576556 

--- K = 8 ---
Median Z.ar:        0.04055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.5622222 
Score segment:      1.287667 

--- K = 9 ---
Median Z.ar:        0.03055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3955556 
Score segment:      1.131 

## Final Score
Final Score: 13.586 
', '\n```'))
```
