---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5094444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      1.186889 

--- K = 2 ---
Median Z.ar:        0.2316667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.534333 

--- K = 3 ---
Median Z.ar:        0.1272222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.638778 

--- K = 4 ---
Median Z.ar:        0.05666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.709333 

--- K = 5 ---
Median Z.ar:        0.03388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.732111 

--- K = 6 ---
Median Z.ar:        0.04555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.9666667 
Score segment:      1.687111 

--- K = 7 ---
Median Z.ar:        0.03777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.8094444 
Score segment:      1.537667 

--- K = 8 ---
Median Z.ar:        0.05611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.4477778 
Score segment:      1.157667 

--- K = 9 ---
Median Z.ar:        0.04833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.46 
Score segment:      1.177667 

## Final Score
Final Score: 13.36156 
', '\n```'))
```
