---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.014444 

--- K = 2 ---
Median Z.ar:        0.2394444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.310556 

--- K = 3 ---
Median Z.ar:        0.1466667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.403333 

--- K = 4 ---
Median Z.ar:        0.075 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.475 

--- K = 5 ---
Median Z.ar:        0.06777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.482222 

--- K = 6 ---
Median Z.ar:        0.1244444 
Median Beta.ar:     1 
Median Gamma.ar:    0.6405556 
Score segment:      1.066111 

--- K = 7 ---
Median Z.ar:        0.09 
Median Beta.ar:     1 
Median Gamma.ar:    0.4227778 
Score segment:      0.9372222 

--- K = 8 ---
Median Z.ar:        0.06055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.5011111 
Score segment:      0.9905556 

--- K = 9 ---
Median Z.ar:        0.4772222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.027222 

## Final Score
Final Score: 10.70667 
', '\n```'))
```
