---
title: "iClusterBayes Summary Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.2\n')
```

# Key Summary Statistics
```{r}
cat(paste0('```\n', '

--- Summary for K = 1 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.4656  0.5028  0.5094  0.5100  0.5178  0.5494 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5783  0.7172  0.6641  0.8061  0.9756 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5622  0.7000  0.6460  0.7844  0.9456 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01778 0.04500 0.07111 0.23762 0.26611 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.02333 0.04611 0.06889 0.20802 0.20569 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01889 0.05278 0.13444 0.33897 0.64000 1.00000 

--- Summary for K = 2 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.1972  0.2244  0.2317  0.2319  0.2394  0.2617 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.3856  0.5617  0.5093  0.6800  0.9428 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.3806  0.5511  0.4928  0.6578  0.9022 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01833 0.44611 0.50474 1.00000 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007778 0.047778 0.330144 0.839306 1.000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.6150  1.0000  0.7689  1.0000  1.0000 

--- Summary for K = 3 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.1011  0.1211  0.1272  0.1280  0.1350  0.1811 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2228  0.4161  0.3840  0.5522  0.9250 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2256  0.4156  0.3762  0.5433  0.8311 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9739  1.0000  0.8363  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0005556 0.0094444 0.2855414 0.7261111 1.0000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5144  1.0000  0.7555  1.0000  1.0000 

--- Summary for K = 4 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.03500 0.05056 0.05667 0.05761 0.06333 0.09278 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1133  0.3311  0.3149  0.4844  0.8978 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1189  0.3378  0.3122  0.4833  0.7911 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9156  1.0000  0.8268  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.000000 0.002222 0.309254 0.920000 1.000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8815  1.0000  1.0000 

--- Summary for K = 5 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01222 0.02778 0.03389 0.03544 0.04278 0.06556 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0650  0.2806  0.2728  0.4272  0.8528 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.06903 0.29222 0.27348 0.43444 0.74667 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.8817  1.0000  0.8288  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.9556  1.0000  1.0000  1.0000  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2931  0.8042  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9544  1.0000  0.8674  1.0000  1.0000 

--- Summary for K = 6 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.02222 0.03833 0.04556 0.04904 0.05722 0.12167 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01333 0.22167 0.22765 0.37611 0.86278 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01444 0.23222 0.22858 0.38444 0.76222 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.05056 0.54333 0.52360 1.00000 1.00000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.7222  1.0000  1.0000  0.9999  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2548  0.5556  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.7300  0.9944  0.7983  1.0000  1.0000 

--- Summary for K = 7 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01778 0.03278 0.03778 0.04047 0.04722 0.08889 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007222 0.162222 0.187225 0.314444 0.807222 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.007778 0.173889 0.188704 0.325556 0.703889 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.3426  0.7911  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.1156  1.0000  1.0000  0.9988  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.00000 0.17191 0.02222 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.5094  0.9306  0.7141  1.0000  1.0000 

--- Summary for K = 8 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.02333 0.04722 0.05611 0.05889 0.06722 0.16111 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.003889 0.115556 0.149403 0.252778 0.765000 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.004444 0.127778 0.154592 0.273333 0.642222 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2951  0.6583  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.9901  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.1028  0.0000  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.3822  0.4109  0.7661  1.0000 

--- Summary for K = 9 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.02500 0.04167 0.04833 0.05010 0.05611 0.12278 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.001111 0.077222 0.136032 0.242778 0.732222 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.001111 0.086667 0.139852 0.260000 0.621111 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2294  0.4683  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9583  1.0000  0.9676  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.1119  0.0000  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.6022  0.5153  0.9061  1.0000 
', '\n```'))
```

# Conclusion
and basic statistics for each K (1–9). The `.png` files show Z.ar, beta.ar, 
and gamma.ar distributions.
