---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2505556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      0.928 

--- K = 2 ---
Median Z.ar:        0.06055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.705444 

--- K = 3 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.741 

--- K = 4 ---
Median Z.ar:        0.006111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.759889 

--- K = 5 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.758778 

--- K = 6 ---
Median Z.ar:        0.008888889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.757111 

--- K = 7 ---
Median Z.ar:        0.01055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8411111 
Score segment:      1.596556 

--- K = 8 ---
Median Z.ar:        0.008333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6844444 
Score segment:      1.442111 

--- K = 9 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.5838889 
Score segment:      1.342667 

## Final Score
Final Score: 14.03156 
', '\n```'))
```
