---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4394444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3777778 
Score segment:      1.115222 

--- K = 2 ---
Median Z.ar:        0.1727778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.593222 

--- K = 3 ---
Median Z.ar:        0.08333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.682667 

--- K = 4 ---
Median Z.ar:        0.055 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.711 

--- K = 5 ---
Median Z.ar:        0.03333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.732667 

--- K = 6 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.741 

--- K = 7 ---
Median Z.ar:        0.04444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.7094444 
Score segment:      1.431 

--- K = 8 ---
Median Z.ar:        0.03388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.4583333 
Score segment:      1.190444 

--- K = 9 ---
Median Z.ar:        0.025 
Median Beta.ar:     1 
Median Gamma.ar:    0.4761111 
Score segment:      1.217111 

## Final Score
Final Score: 13.41433 
', '\n```'))
```
