---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 2.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7127778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3777778 
Score segment:      1.388556 

--- K = 2 ---
Median Z.ar:        0.495 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.793 

--- K = 3 ---
Median Z.ar:        0.39 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.688 

--- K = 4 ---
Median Z.ar:        0.4127778 
Median Beta.ar:     1 
Median Gamma.ar:    0.8227778 
Score segment:      1.533556 

--- K = 5 ---
Median Z.ar:        0.34 
Median Beta.ar:     1 
Median Gamma.ar:    0.6533333 
Score segment:      1.291333 

--- K = 6 ---
Median Z.ar:        0.2961111 
Median Beta.ar:     1 
Median Gamma.ar:    0.5655556 
Score segment:      1.159667 

--- K = 7 ---
Median Z.ar:        0.7438889 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.509889 

--- K = 8 ---
Median Z.ar:        0.6861111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.452111 

--- K = 9 ---
Median Z.ar:        0.5127778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.278778 

## Final Score
Final Score: 13.09489 
', '\n```'))
```
