---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4427778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      0.9583333 

--- K = 2 ---
Median Z.ar:        0.1866667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.363333 

--- K = 3 ---
Median Z.ar:        0.08555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.464444 

--- K = 4 ---
Median Z.ar:        0.04722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.502778 

--- K = 5 ---
Median Z.ar:        0.03722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.512778 

--- K = 6 ---
Median Z.ar:        0.06444444 
Median Beta.ar:     1 
Median Gamma.ar:    0.75 
Score segment:      1.235556 

--- K = 7 ---
Median Z.ar:        0.03055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8288889 
Score segment:      1.348333 

--- K = 8 ---
Median Z.ar:        0.04944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.4611111 
Score segment:      0.9616667 

--- K = 9 ---
Median Z.ar:        0.09111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.1211111 
Score segment:      1.237778 

## Final Score
Final Score: 11.585 
', '\n```'))
```
