---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.4405556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      1.118 

--- K = 2 ---
Median Z.ar:        0.17 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.596 

--- K = 3 ---
Median Z.ar:        0.05611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.709889 

--- K = 4 ---
Median Z.ar:        0.04222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.723778 

--- K = 5 ---
Median Z.ar:        0.03 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.736 

--- K = 6 ---
Median Z.ar:        0.01944444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.746556 

--- K = 7 ---
Median Z.ar:        0.035 
Median Beta.ar:     1 
Median Gamma.ar:    0.8161111 
Score segment:      1.547111 

--- K = 8 ---
Median Z.ar:        0.03111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.57 
Score segment:      1.304889 

--- K = 9 ---
Median Z.ar:        0.02277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6277778 
Score segment:      1.371 

## Final Score
Final Score: 13.85322 
', '\n```'))
```
