---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.005, beta.var.scale = 1.25\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.8466667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3744444 
Score segment:      1.519111 

--- K = 2 ---
Median Z.ar:        0.7688889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      2.066889 

--- K = 3 ---
Median Z.ar:        0.6766667 
Median Beta.ar:     1 
Median Gamma.ar:    0.8183333 
Score segment:      1.793 

--- K = 4 ---
Median Z.ar:        0.6605556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3638889 
Score segment:      1.322444 

--- K = 5 ---
Median Z.ar:        0.7094444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.475444 

--- K = 6 ---
Median Z.ar:        0.7677778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.533778 

--- K = 7 ---
Median Z.ar:        0.9772222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.743222 

--- K = 8 ---
Median Z.ar:        0.8927778 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.658778 

--- K = 9 ---
Median Z.ar:        0.9866667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.752667 

## Final Score
Final Score: 14.86533 
', '\n```'))
```
