---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.3822222 
Score segment:      1.063556 

--- K = 2 ---
Median Z.ar:        0.1333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.632667 

--- K = 3 ---
Median Z.ar:        0.05055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.715444 

--- K = 4 ---
Median Z.ar:        0.015 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.751 

--- K = 5 ---
Median Z.ar:        0.01722222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.748778 

--- K = 6 ---
Median Z.ar:        0.01833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.747667 

--- K = 7 ---
Median Z.ar:        0.01611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9438889 
Score segment:      1.693778 

--- K = 8 ---
Median Z.ar:        0.01333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8833333 
Score segment:      1.636 

--- K = 9 ---
Median Z.ar:        0.02388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.5194444 
Score segment:      1.261556 

## Final Score
Final Score: 14.25044 
', '\n```'))
```
