---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 0.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3877778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04944444 
Score segment:      1.012778 

--- K = 2 ---
Median Z.ar:        0.1377778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.412222 

--- K = 3 ---
Median Z.ar:        0.05555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.494444 

--- K = 4 ---
Median Z.ar:        0.02055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.529444 

--- K = 5 ---
Median Z.ar:        0.02222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.527778 

--- K = 6 ---
Median Z.ar:        0.015 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.535 

--- K = 7 ---
Median Z.ar:        0.01833333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8744444 
Score segment:      1.406111 

--- K = 8 ---
Median Z.ar:        0.02944444 
Median Beta.ar:     1 
Median Gamma.ar:    0.6194444 
Score segment:      1.14 

--- K = 9 ---
Median Z.ar:        0.02333333 
Median Beta.ar:     1 
Median Gamma.ar:    0.4588889 
Score segment:      0.9855556 

## Final Score
Final Score: 12.04333 
', '\n```'))
```
