---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6005556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3811111 
Score segment:      1.279667 

--- K = 2 ---
Median Z.ar:        0.3727778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.670778 

--- K = 3 ---
Median Z.ar:        0.1933333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.572667 

--- K = 4 ---
Median Z.ar:        0.1316667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.634333 

--- K = 5 ---
Median Z.ar:        0.1161111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9372222 
Score segment:      1.587111 

--- K = 6 ---
Median Z.ar:        0.105 
Median Beta.ar:     1 
Median Gamma.ar:    0.7927778 
Score segment:      1.453778 

--- K = 7 ---
Median Z.ar:        0.1033333 
Median Beta.ar:     1 
Median Gamma.ar:    0.6627778 
Score segment:      1.325444 

--- K = 8 ---
Median Z.ar:        0.1527778 
Median Beta.ar:     1 
Median Gamma.ar:    0.4038889 
Score segment:      1.017111 

--- K = 9 ---
Median Z.ar:        0.525 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.291 

## Final Score
Final Score: 12.83189 
', '\n```'))
```
