---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6027778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04888889 
Score segment:      1.103889 

--- K = 2 ---
Median Z.ar:        0.3405556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.209444 

--- K = 3 ---
Median Z.ar:        0.25 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.3 

--- K = 4 ---
Median Z.ar:        0.1144444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.435556 

--- K = 5 ---
Median Z.ar:        0.1188889 
Median Beta.ar:     1 
Median Gamma.ar:    0.8972222 
Score segment:      1.328333 

--- K = 6 ---
Median Z.ar:        0.4533333 
Median Beta.ar:     1 
Median Gamma.ar:    0.1133333 
Score segment:      0.89 

--- K = 7 ---
Median Z.ar:        0.525 
Median Beta.ar:     1 
Median Gamma.ar:    0.01555556 
Score segment:      1.059444 

--- K = 8 ---
Median Z.ar:        0.4466667 
Median Beta.ar:     1 
Median Gamma.ar:    0.01333333 
Score segment:      0.99 

--- K = 9 ---
Median Z.ar:        0.9494444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.499444 

## Final Score
Final Score: 10.81611 
', '\n```'))
```
