---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.2494444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3816667 
Score segment:      0.9291111 

--- K = 2 ---
Median Z.ar:        0.05833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.707667 

--- K = 3 ---
Median Z.ar:        0.015 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.751 

--- K = 4 ---
Median Z.ar:        0.01111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.754889 

--- K = 5 ---
Median Z.ar:        0.01111111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.754889 

--- K = 6 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.758778 

--- K = 7 ---
Median Z.ar:        0.007222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.758778 

--- K = 8 ---
Median Z.ar:        0.006111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9161111 
Score segment:      1.676 

--- K = 9 ---
Median Z.ar:        0.01 
Median Beta.ar:     1 
Median Gamma.ar:    0.3572222 
Score segment:      1.113222 

## Final Score
Final Score: 14.20433 
', '\n```'))
```
