---
title: "iClusterBayes Summary Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.05, beta.var.scale = 1\n')
```

# Key Summary Statistics
```{r}
cat(paste0('```\n', '

--- Summary for K = 1 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.2194  0.2439  0.2517  0.2517  0.2589  0.2889 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.09833 0.14111 0.13813 0.17222 0.88278 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1022  0.1450  0.1418  0.1767  0.7239 
  Modality 2 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.005000 0.008333 0.101992 0.031111 1.000000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.005000 0.008333 0.077249 0.023889 1.000000 
  Modality 5 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.006111 0.015000 0.162307 0.118333 1.000000 

--- Summary for K = 2 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.04278 0.05944 0.06333 0.06315 0.06722 0.08722 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.06333 0.10833 0.11277 0.14722 0.89667 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.06625 0.11278 0.11623 0.15222 0.67167 
  Modality 2 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.001667 0.060000 0.415376 1.000000 1.000000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0005556 0.0050000 0.2483599 0.3805556 1.0000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1294  1.0000  0.6982  1.0000  1.0000 

--- Summary for K = 3 ---
Z.ar:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01444 0.02611 0.03056 0.03089 0.03500 0.05833 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.02667 0.07056 0.07914 0.11278 0.85222 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.02778 0.07444 0.08240 0.11778 0.60833 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9189  1.0000  0.7933  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0000000 0.0000000 0.0005556 0.2238627 0.1551389 1.0000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.05389 1.00000 0.67336 1.00000 1.00000 

--- Summary for K = 4 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.002222 0.007778 0.009444 0.010160 0.012222 0.030556 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.03056 0.06667 0.07649 0.10389 0.82667 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.03333 0.07111 0.08063 0.11111 0.68667 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9361  1.0000  0.7971  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2543  0.5308  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8425  1.0000  1.0000 

--- Summary for K = 5 ---
Z.ar:
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0005556 0.0050000 0.0072222 0.0076276 0.0094444 0.0466667 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.02111 0.05778 0.06776 0.09611 0.76111 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.02333 0.06333 0.07259 0.10389 0.59111 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.6694  1.0000  0.7711  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2873  0.9133  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.8982  1.0000  1.0000 

--- Summary for K = 6 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.001111 0.006667 0.008333 0.008843 0.010556 0.027778 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01278 0.04667 0.05972 0.08556 0.79111 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01444 0.05111 0.06395 0.09333 0.57056 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.3372  0.4553  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.8917  1.0000  1.0000  1.0000  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2276  0.3649  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.9194  1.0000  0.8313  1.0000  1.0000 

--- Summary for K = 7 ---
Z.ar:
     Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
0.0005556 0.0044444 0.0061111 0.0067271 0.0083333 0.0250000 

beta.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01056 0.03778 0.05240 0.07444 0.75944 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01222 0.04222 0.05722 0.08333 0.52333 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0500  0.4181  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.000000 0.000000 0.204194 0.008194 1.000000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.6533  1.0000  0.7649  1.0000  1.0000 

--- Summary for K = 8 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.001111 0.005556 0.007778 0.008400 0.010556 0.034444 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.008889 0.036667 0.053713 0.076111 0.763333 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.01000 0.04222 0.05841 0.08667 0.50833 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.1400  0.4153  1.0000  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.4972  1.0000  1.0000  1.0000  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.1802  0.0000  1.0000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.3544  0.9178  0.6819  1.0000  1.0000 

--- Summary for K = 9 ---
Z.ar:
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.003333 0.008333 0.010556 0.010679 0.012778 0.027222 

beta.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.001667 0.016111 0.034721 0.050000 0.671667 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      1       1       1       1       1       1 

gamma.ar:
  Modality 1 :
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.002222 0.018889 0.038832 0.058333 0.446667 
  Modality 2 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.0000  0.2846  0.6339  1.0000 
  Modality 3 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  1.0000  1.0000  0.9865  1.0000  1.0000 
  Modality 4 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.00000 0.00000 0.06503 0.00000 1.00000 
  Modality 5 :
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.3939  0.4465  0.9556  1.0000 
', '\n```'))
```

# Conclusion
This brief report includes acceptance rate summaries, posterior probabilities, 
and basic statistics for each K (1–9). The `.png` files show Z.ar, beta.ar, 
and gamma.ar distributions.
