---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6005556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3772222 
Score segment:      1.275778 

--- K = 2 ---
Median Z.ar:        0.37 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.668 

--- K = 3 ---
Median Z.ar:        0.1816667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.584333 

--- K = 4 ---
Median Z.ar:        0.1244444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.641556 

--- K = 5 ---
Median Z.ar:        0.1161111 
Median Beta.ar:     1 
Median Gamma.ar:    0.9177778 
Score segment:      1.567667 

--- K = 6 ---
Median Z.ar:        0.1155556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8411111 
Score segment:      1.491556 

--- K = 7 ---
Median Z.ar:        0.1677778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3611111 
Score segment:      0.9593333 

--- K = 8 ---
Median Z.ar:        0.1616667 
Median Beta.ar:     1 
Median Gamma.ar:    0.4027778 
Score segment:      1.007111 

--- K = 9 ---
Median Z.ar:        0.1594444 
Median Beta.ar:     1 
Median Gamma.ar:    0.2827778 
Score segment:      0.8893333 

## Final Score
Final Score: 12.08467 
', '\n```'))
```
