---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.015, beta.var.scale = 0.1\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.6027778 
Median Beta.ar:     1 
Median Gamma.ar:    0.04777778 
Score segment:      1.105 

--- K = 2 ---
Median Z.ar:        0.3394444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.210556 

--- K = 3 ---
Median Z.ar:        0.1666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.383333 

--- K = 4 ---
Median Z.ar:        0.12 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.43 

--- K = 5 ---
Median Z.ar:        0.2727778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6116667 
Score segment:      0.8888889 

--- K = 6 ---
Median Z.ar:        0.1227778 
Median Beta.ar:     1 
Median Gamma.ar:    0.7433333 
Score segment:      1.170556 

--- K = 7 ---
Median Z.ar:        0.1661111 
Median Beta.ar:     1 
Median Gamma.ar:    0.4111111 
Score segment:      0.8727778 

--- K = 8 ---
Median Z.ar:        0.6255556 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.175556 

--- K = 9 ---
Median Z.ar:        0.9572222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.507222 

## Final Score
Final Score: 10.74389 
', '\n```'))
```
