---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7144444 
Median Beta.ar:     1 
Median Gamma.ar:    0.04833333 
Score segment:      1.216111 

--- K = 2 ---
Median Z.ar:        0.5661111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.216111 

--- K = 3 ---
Median Z.ar:        0.4172222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.132778 

--- K = 4 ---
Median Z.ar:        0.5816667 
Median Beta.ar:     1 
Median Gamma.ar:    0.4422222 
Score segment:      0.6894444 

--- K = 5 ---
Median Z.ar:        0.7644444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.314444 

--- K = 6 ---
Median Z.ar:        0.7144444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.264444 

--- K = 7 ---
Median Z.ar:        0.9533333 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.503333 

--- K = 8 ---
Median Z.ar:        0.9866667 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.536667 

--- K = 9 ---
Median Z.ar:        0.8772222 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.427222 

## Final Score
Final Score: 11.30056 
', '\n```'))
```
