---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.01, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.7116667 
Median Beta.ar:     1 
Median Gamma.ar:    0.3794444 
Score segment:      1.389111 

--- K = 2 ---
Median Z.ar:        0.5705556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.868556 

--- K = 3 ---
Median Z.ar:        0.4316667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.729667 

--- K = 4 ---
Median Z.ar:        0.3933333 
Median Beta.ar:     1 
Median Gamma.ar:    0.8944444 
Score segment:      1.585778 

--- K = 5 ---
Median Z.ar:        0.4316667 
Median Beta.ar:     1 
Median Gamma.ar:    0.5222222 
Score segment:      1.251889 

--- K = 6 ---
Median Z.ar:        0.3827778 
Median Beta.ar:     1 
Median Gamma.ar:    0.3488889 
Score segment:      1.029667 

--- K = 7 ---
Median Z.ar:        0.4533333 
Median Beta.ar:     1 
Median Gamma.ar:    0.1005556 
Score segment:      1.118778 

--- K = 8 ---
Median Z.ar:        0.8594444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.625444 

--- K = 9 ---
Median Z.ar:        0.8211111 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.587111 

## Final Score
Final Score: 13.186 
', '\n```'))
```
