---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5111111 
Median Beta.ar:     1 
Median Gamma.ar:    0.3805556 
Score segment:      1.189667 

--- K = 2 ---
Median Z.ar:        0.2411111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.539111 

--- K = 3 ---
Median Z.ar:        0.125 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.641 

--- K = 4 ---
Median Z.ar:        0.05555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.710444 

--- K = 5 ---
Median Z.ar:        0.04055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.725444 

--- K = 6 ---
Median Z.ar:        0.06 
Median Beta.ar:     1 
Median Gamma.ar:    0.8761111 
Score segment:      1.582111 

--- K = 7 ---
Median Z.ar:        0.05388889 
Median Beta.ar:     1 
Median Gamma.ar:    0.7494444 
Score segment:      1.461556 

--- K = 8 ---
Median Z.ar:        0.04611111 
Median Beta.ar:     1 
Median Gamma.ar:    0.6611111 
Score segment:      1.381 

--- K = 9 ---
Median Z.ar:        0.08055556 
Median Beta.ar:     1 
Median Gamma.ar:    0.3866667 
Score segment:      1.072111 

## Final Score
Final Score: 13.30244 
', '\n```'))
```
