---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 0.3\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5133333 
Median Beta.ar:     1 
Median Gamma.ar:    0.04777778 
Score segment:      1.015556 

--- K = 2 ---
Median Z.ar:        0.24 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.31 

--- K = 3 ---
Median Z.ar:        0.09555556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.454444 

--- K = 4 ---
Median Z.ar:        0.08388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.466111 

--- K = 5 ---
Median Z.ar:        0.06777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.9766667 
Score segment:      1.458889 

--- K = 6 ---
Median Z.ar:        0.04555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.895 
Score segment:      1.399444 

--- K = 7 ---
Median Z.ar:        0.4933333 
Median Beta.ar:     1 
Median Gamma.ar:    0.02444444 
Score segment:      1.018889 

--- K = 8 ---
Median Z.ar:        0.4222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.005 
Score segment:      1.022778 

--- K = 9 ---
Median Z.ar:        0.4544444 
Median Beta.ar:     1 
Median Gamma.ar:    0 
Score segment:      1.004444 

## Final Score
Final Score: 11.15056 
', '\n```'))
```
