---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.03, beta.var.scale = 2.5\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.3844444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3827778 
Score segment:      1.065222 

--- K = 2 ---
Median Z.ar:        0.1477778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.618222 

--- K = 3 ---
Median Z.ar:        0.05277778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.713222 

--- K = 4 ---
Median Z.ar:        0.02333333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.742667 

--- K = 5 ---
Median Z.ar:        0.035 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.731 

--- K = 6 ---
Median Z.ar:        0.01777778 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.748222 

--- K = 7 ---
Median Z.ar:        0.01444444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.751556 

--- K = 8 ---
Median Z.ar:        0.01222222 
Median Beta.ar:     1 
Median Gamma.ar:    0.9244444 
Score segment:      1.678222 

--- K = 9 ---
Median Z.ar:        0.02166667 
Median Beta.ar:     1 
Median Gamma.ar:    0.4 
Score segment:      1.144333 

## Final Score
Final Score: 14.19267 
', '\n```'))
```
