---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.02, beta.var.scale = 2\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.5094444 
Median Beta.ar:     1 
Median Gamma.ar:    0.3788889 
Score segment:      1.186333 

--- K = 2 ---
Median Z.ar:        0.2311111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.534889 

--- K = 3 ---
Median Z.ar:        0.1388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.627111 

--- K = 4 ---
Median Z.ar:        0.05666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.709333 

--- K = 5 ---
Median Z.ar:        0.04055556 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.725444 

--- K = 6 ---
Median Z.ar:        0.04388889 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.722111 

--- K = 7 ---
Median Z.ar:        0.04555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.8194444 
Score segment:      1.539889 

--- K = 8 ---
Median Z.ar:        0.05277778 
Median Beta.ar:     1 
Median Gamma.ar:    0.4788889 
Score segment:      1.192111 

--- K = 9 ---
Median Z.ar:        0.09555556 
Median Beta.ar:     1 
Median Gamma.ar:    0.4022222 
Score segment:      1.072667 

## Final Score
Final Score: 13.30989 
', '\n```'))
```
