---
title: "Robust Metrics Report"
author: "Automated Report"
output: pdf_document
---

# Hyperparameters
```{r}
cat('sdev = 0.025, beta.var.scale = 1.25\n')
```

# Robust Metrics & Score
```{r}
cat(paste0('```\n', '
## Per-K Metrics

--- K = 1 ---
Median Z.ar:        0.44 
Median Beta.ar:     1 
Median Gamma.ar:    0.3816667 
Score segment:      1.119667 

--- K = 2 ---
Median Z.ar:        0.1744444 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.591556 

--- K = 3 ---
Median Z.ar:        0.09222222 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.673778 

--- K = 4 ---
Median Z.ar:        0.04833333 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.717667 

--- K = 5 ---
Median Z.ar:        0.02611111 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.739889 

--- K = 6 ---
Median Z.ar:        0.03 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.736 

--- K = 7 ---
Median Z.ar:        0.01666667 
Median Beta.ar:     1 
Median Gamma.ar:    1 
Score segment:      1.749333 

--- K = 8 ---
Median Z.ar:        0.03777778 
Median Beta.ar:     1 
Median Gamma.ar:    0.6 
Score segment:      1.328222 

--- K = 9 ---
Median Z.ar:        0.03722222 
Median Beta.ar:     1 
Median Gamma.ar:    0.3566667 
Score segment:      1.085444 

## Final Score
Final Score: 13.74156 
', '\n```'))
```
